---
title: "Incivility and Representation"
subtitle: Abbildungen und Tabellen
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
classoption: landscape
bibliography: literatur.bibtex
always_allow_html: yes
editor_options:
  chunk_output_type: console
---

```{r load_libraries, message = FALSE, echo = FALSE}
library(dplyr)
library(magrittr)
library(tidyr)
library(forcats)
library(haven)
library(crosstable)
library(scales)
library(ggplot2)
library(flextable)
library(openxlsx)
library(ggplot2)
library(kommrep)
library(xtable)
library(stargazer)
library(jtools)
library(broom.mixed) # to avoid later msg of loading
library(officer)
library(ggpubr)
library(kableExtra)

stopifnot(packageVersion("kommrep") >= package_version("0.4.1"))
```

```{r set_options, include = FALSE}
set_flextable_defaults(pct_digits = "#")
options("modelsummary_format_numeric_latex" = "plain")
```

```{r make modified_table, echo = FALSE, results = "asis"}
source("~/Lab/github/incivility/aux/kommrep_loc_lm.R")

kommrep_loc %>% 
  haven::write_dta(path = "~/Lab/github/incivility/dta/kommrep_loc_lm.dta")
```


## Research design

### Table 1: Response Rate

```{r return_rate, echo = FALSE}
db_final_fname <- "~/Data/hbs/db/HBS-Kontaktdatenbank_2022-07-21.xlsx"
db <- openxlsx::read.xlsx(xlsxFile = db_final_fname) %>% 
  filter(!is.na(Name)) %>% 
  unique()

n_representatives <- db %>% 
  nrow()

n_representatives_nomail <- db %>% 
  filter(is.na(Mailadresse)) %>% 
  nrow()

participants <- tibble(
  `population (total)` = n_representatives,
  `representatives no contact details` = sprintf(
    "%d (%g per cent)",
    n_representatives_nomail,
    round(n_representatives_nomail / n_representatives * 100, 1)
  )
)

termination_rate <- 100 - round(nrow(kommrep_loc) / nrow(kommrep) * 100, 1)
participation_rate_started <- percent(nrow(kommrep) / nrow(filter(mailout, run == 0)), accuracy = 0.1)
participation_rate_finished <- percent(nrow(kommrep_loc) / nrow(filter(mailout, run == 0)), accuracy = 0.1)

returned <- tibble(
  `Response\n(total)` = nrow(kommrep), # paper #1: 2592
  `Fully completed` = nrow(filter(kommrep, v_lastpage == 40)),
  `partially completed` = nrow(kommrep) - nrow(filter(kommrep, v_lastpage == 40)),
   # paper #1: 2166
  `Net response rate` = participation_rate_finished, 
  `Response rate` = participation_rate_started
)

flextable(returned)
```

\newpage

## Section 4: Empirical Evidence

### Figure 1: Prevalence of the implications for representation 

```{r implications, echo = FALSE}
kommrep_loc %>%
  mutate(`behavior_considering exit?` = as.character(as_factor(v_exit))) %>%
  mutate(`behavior_considering exit?` = recode(
    `behavior_considering exit?`,
    `Ja` = "yes",
    `Nein` = "no",
    "Weiß nicht" = "don't know / missing"
  )) %>%
  mutate(`behavior_considering exit?` = ifelse(
    is.na(`behavior_considering exit?`),
    "don't know / missing",
    `behavior_considering exit?`
  )) %>%
  mutate(`behavior_avoid topics?` = as.character(as_factor(v_sorge_umgang4))) %>%
  mutate(`behavior_avoid topics?` = recode(
    `behavior_avoid topics?`,
    `Ja` = "yes",
    `Nicht Gewählt` = "no",
    `Weiß nicht` = "don't know / missing"
  )) %>%
  mutate(`behavior_avoid topics?` = ifelse(
    is.na(`behavior_avoid topics?`),
    "don't know / missing",
    `behavior_avoid topics?`
  )) %>%
  select(starts_with("behavior_"), weight_ps) %>%
  pivot_longer(cols = starts_with("behavior")) %>%
  mutate(name = gsub("^behavior_(.*?)$", "\\1", name)) %>%
  group_by(name, value) %>%
  summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
  pivot_wider(names_from = value, values_from = n_weighed) %>%
  mutate(true_percent = `yes` / (`yes` + `no` + `don't know / missing`)) %>%
  mutate(false_percent = `no` / (`yes` + `no` + `don't know / missing`)) %>%
  mutate(na_percent = `don't know / missing` / (`yes` + `no` + `don't know / missing`)) %>%
  mutate(name = factor(name, levels = c("considering exit?", "avoid topics?"))) %>%
  select(- `no`, -`yes`, -`don't know / missing`) %>%
  rename(
    `what` = "name",
    `yes` = "true_percent",
    `no` = "false_percent",
    `don't know / missing` = "na_percent"
  ) %>%
  pivot_longer(cols = c("yes", "don't know / missing", "no")) %>%
  mutate(name = factor(name, levels = c("no", "don't know / missing", "yes"))) %>%
  ggplot(aes(x = what, y = value, fill = name)) +
    geom_bar(stat = "identity", position = "stack") + 
    geom_text(
    aes(label = paste0(round(value * 100, 1), "%")),
    position = position_stack(0.5),    # move to center of bars
     size = 4, color = "white",
    lineheight = 1
    ) + 
    xlab("Consequences of threats") + 
    ylab("Share/percent (based on weighed cases)") +
    theme(
      legend.title = element_blank(),
      axis.title = element_text(size = 12),
      axis.text = element_text(size = 10)
    ) +
   scale_y_continuous(labels = scales::percent) +
   scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5])

ggsave("~/Lab/github/incivility/svg/behavioral_change.jpg", width = 24, height = 12, units = "cm")
```

\newpage

```{r implications_old, echo = FALSE}
kommrep_loc %>%
  select(
    v_sorge_umgang1, # 1 = Ich habe mein Verhalten nicht geändert
    v_sorge_umgang2, # 2 = Ich bin gegenüber meiner Umgebung misstrauischer / vorsichtiger.
    v_sorge_umgang3, # 3 = Ich verzichte (weitgehend) auf die Nutzung sozialer Medien
    v_sorge_umgang4, # 4 = Ich äußere mich zu be- stimmten Themen seltener als früher
    v_sorge_umgang5, # 5 = Ich meide bestimmte Orte oder Veranstaltungen
    v_sorge_umgang6, # 6 = Ich habe meinen Wohnort geändert
    weight_ps
  ) %>%
  pivot_longer(cols = starts_with("v_sorge_umgang")) %>%
  group_by(name, value) %>%
  summarise(n_weighed = sum(weight_ps)) %>%
  filter(value == 1) %>%
  mutate(share = round(n_weighed / sum(kommrep_loc$weight_ps) * 100, 1))
```



### Table: Plain Shares

```{r plain_shares, results = "asis", echo=FALSE}
kommrep_loc_lm %>%
  select(
    threat_verbal, threat_physical,
    threat_verbal_bin, threat_physical_bin,
    female_diverse,
    class,
    racialized,
    soc, gen, div,
    weight_ps
  ) %>%
  select(-threat_verbal, -threat_physical) %>%
  
  mutate(class_lower = ifelse(class == "lower", TRUE, FALSE)) %>%
  
  # select(-weight_ps) %>%
  mutate(across(everything(), as.vector)) %>%
  pivot_longer(cols = c(threat_verbal_bin, threat_physical_bin, racialized, female_diverse, class_lower, div, gen, soc)) %>%
  group_by(name, value) %>%
  summarise(n = n(), n_weighed = sum(weight_ps), .groups = "rowwise") %>%
  select(-n) %>%
  pivot_wider(names_from = value, values_from = c(n_weighed)) %>%
  ungroup() %>%
  mutate(total = apply(as.matrix(select(., `FALSE`, `TRUE`, `NA`)), 1, sum, na.rm = TRUE)) %>%
  mutate(
    true = round(`TRUE` / total * 100, 1),
    na = round(`NA` / total * 100, 1),
    false = round(`FALSE` / total * 100, 1)
  ) %>%
  mutate(missing = ifelse(is.na(na), 0, na)) %>%
  select(name, true, missing, false) %>%
  mutate(variable = as.factor(name)) %>%
  select(-name) %>%
  mutate(variable = forcats::fct_recode(
    variable,
    `Communicative threat` = "threat_verbal_bin",
    `Physical threat` = "threat_physical_bin",
    `Racialized group` = "racialized",
    `Female or diverse` = "female_diverse",
    `Class lower` = "class_lower",
    `Primary Topic: Migration` = "div",
    `Primary Topic: Gender` = "gen",
    `Primary Topic: Class` = "soc"
  )) %>%
  mutate(
    variable = factor(
      variable,
      levels = c(
        "Communicative threat", "Physical threat",
        "Racialized group", "Female or diverse", "Class lower",
        "Primary Topic: Migration", "Primary Topic: Gender", "Primary Topic: Class"
      )
    )
  ) %>%
  mutate(
    true = paste0(true, "%"),
    missing = paste0(missing, "%"),
    false = paste0(false, "%")
  ) %>%
  mutate(missing = ifelse(missing == "0%", "---", missing)) %>%
  arrange(variable) %>%
  relocate(variable) %>% 
  as_flextable(show_coltype = FALSE) %>%
  add_footer_lines("* Percent/shares calculated using case weights")
```

\newpage

### Figure 2: Threat experience and implications for representation

```{r threat_and_change3, echo = FALSE}
threat_and_change <- kommrep_loc_lm %>%
#  mutate(weight_ps = 1) %>%
  select(threat_verbal, threat_physical, muted2, stay, weight_ps) %>%
  
  mutate(stay = ifelse(is.na(stay), FALSE, stay)) %>%
  
  mutate(`communicative threat` = ifelse(threat_verbal > 0, "yes", "no/missing")) %>% 
  mutate(`communicative threat` = ifelse(is.na(`communicative threat`), "no/missing", `communicative threat`)) %>% 
  
  mutate(`physical threat` = ifelse(threat_physical > 0, "yes", "no/missing")) %>% 
  mutate(`physical threat` = ifelse(is.na(`physical threat`), "no/missing", `physical threat`)) %>% 
  
  select(
    `communicative threat`, `physical threat`,
    `muted2`, `stay`,
    `weight_ps`
  )


table_data <- bind_cols(
  list(
    bind_rows(
      list(
        threat_and_change %>%
          select(`stay`, `communicative threat`, weight_ps) %>%
          group_by(`stay`, `communicative threat`) %>%
          summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
          group_by(`communicative threat`) %>%
          group_split() %>%
          lapply(function(tbl) mutate(tbl, percent = round(n_weighed / sum(n_weighed) * 100, 1))) %>%
          bind_rows() %>%
          mutate(percent = sprintf("%s\n(%s)", paste0(percent, "%"), round(n_weighed, 1))) %>%
          select(-n_weighed) %>%
          pivot_wider(names_from = "stay", values_from = "percent") %>%
          rename(`threat` = "communicative threat") %>%
          mutate(threat_type = "communicative threat") %>%
          relocate(threat_type),
        
        threat_and_change %>%
          select(`stay`, `physical threat`, weight_ps) %>%
          group_by(`stay`, `physical threat`) %>%
          summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
          group_by(`physical threat`) %>%
          group_split() %>%
          lapply(function(tbl) mutate(tbl, percent = round(n_weighed / sum(n_weighed) * 100, 1))) %>%
          bind_rows() %>%
          mutate(percent = sprintf("%s\n(%s)", paste0(percent, "%"), round(n_weighed, 1))) %>%
          select(-n_weighed) %>%
          pivot_wider(names_from = "stay", values_from = "percent") %>%
          rename(`threat` = "physical threat") %>%
          mutate(threat_type = "physical threat") %>%
          relocate(threat_type)
      )
    ),
    bind_rows(
      list(
        threat_and_change %>%
          select(`muted2`, `communicative threat`, weight_ps) %>%
          group_by(`muted2`, `communicative threat`) %>%
          summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
          group_by(`communicative threat`) %>%
          group_split() %>%
          lapply(function(tbl) mutate(tbl, percent = round(n_weighed / sum(n_weighed) * 100, 1))) %>%
          bind_rows() %>%
          mutate(percent = sprintf("%s\n(%s)", paste0(percent, "%"), round(n_weighed, 1))) %>%
          select(-n_weighed) %>%
          pivot_wider(names_from = "muted2", values_from = "percent") %>%
          select(-`communicative threat`), 
        
        threat_and_change %>%
          select(`muted2`, `physical threat`, weight_ps) %>%
          group_by(`muted2`, `physical threat`) %>%
          summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
          group_by(`physical threat`) %>%
          group_split() %>%
          lapply(function(tbl) mutate(tbl, percent = round(n_weighed / sum(n_weighed) * 100, 1))) %>%
          bind_rows() %>%
          mutate(percent = sprintf("%s\n(%s)", paste0(percent, "%"), round(n_weighed, 1))) %>%
          select(-n_weighed) %>%
          pivot_wider(names_from = "muted2", values_from = "percent") %>%
          select(-`physical threat`)
      )
    )
  )
) 

m <- table_data %>%
  select(-threat_type, -threat) %>%
  mutate(across(everything(), function(x) as.numeric(gsub("^.*?\\((.*)\\)$", "\\1", x))))

chisq.test(m[1:2, 1:2]) # X-squared = 28.246, df = 1, p-value = 1.068e-07
chisq.test(m[3:4, 1:2]) # X-squared = 23.077, df = 1, p-value = 1.557e-06
chisq.test(m[1:2, 3:4]) # X-squared = 19.208, df = 1, p-value = 1.172e-05
chisq.test(m[3:4, 3:4]) # X-squared = 7.2755, df = 1, p-value = 0.00699

table_data %>% 
  as_flextable(show_coltype = FALSE) %>%
  merge_at(i = 1:2, j = 1) %>%
  merge_at(i = 3:4, j = 1) %>%
  set_header_labels(
    values = c(
      `threat_type` = "",
      `threat` = "",
      `FALSE...3` = "no",
      `TRUE...4` = "yes",
      `FALSE...5` = "no",
      `TRUE...6` = "yes"
    )
  ) %>%
  add_header_row(
    top = TRUE,
    values = c("", "", "certainty to stay", "avoid topics"),
    colwidths = c(1,1, 2,2)
  ) %>% 
  hline(i = 2) %>%
  flextable::align(i = 1:2, j = 3:6, align = "center", part = "header") %>%
  fix_border_issues(part = "all") %>%
  hline_bottom(part = "footer") %>%
  add_footer_lines("* Value in brackets: Weighted number of cases")
```



\newpage

### Figure 3: Certain descriptive characteristics and consider exit 

```{r, echo = FALSE}
GENDER <- kommrep_loc_lm %>%
  select(v_exit, v_geschlecht, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(exit = as.character(as_factor(v_exit))) %>%
  mutate(exit = recode(
    exit,
    `Ja` = "yes",
    `Nein` = "no",
    "Weiß nicht" = "don't know / missing"
  )) %>%
  mutate(exit = ifelse(is.na(exit), "don't know / missing", exit)) %>%
  mutate(gender = as_factor(v_geschlecht)) %>%
  mutate(gender = recode(
    gender,
    `männlich` = "male",
    `weiblich` = "female/diverse",
    `divers` = "female/diverse",
    `weitere / andere` = "female/diverse")
  ) %>%
  mutate(gender = factor(gender, levels = c("male", "female/diverse"))) %>%
  select(gender, `exit`, weight_ps, threat_experience) %>%
  group_by(gender, `exit`, threat_experience) %>%
  filter(!is.na(gender)) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(gender, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(exit = factor(exit, levels = c("no", "don't know / missing", "yes"))) %>%
  ggplot(aes(x = gender, y = share, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

RACE <- kommrep_loc_lm %>%
  select(v_exit, racialized, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(exit = as.character(as_factor(v_exit))) %>%
  mutate(exit = recode(
    exit,
    `Ja` = "yes",
    `Nein` = "no",
    "Weiß nicht" = "don't know / missing"
  )) %>%
  mutate(exit = ifelse(is.na(exit), "don't know / missing", exit)) %>%
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  filter(!is.na(`racialized`)) %>%
  group_by(`racialized`, `exit`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`racialized`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(exit = factor(exit, levels = c("no", "don't know / missing", "yes"))) %>%
  ggplot(aes(x = `racialized`, y = share, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) +
    ylab("percent (based on weighed cases)")

CLASS <- kommrep_loc_lm %>%
  select(v_exit, class, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(exit = as.character(as_factor(v_exit))) %>%
  mutate(exit = recode(
    exit,
    `Ja` = "yes",
    `Nein` = "no",
    "Weiß nicht" = "don't know / missing"
  )) %>%
  mutate(exit = ifelse(is.na(exit), "don't know / missing", exit)) %>%
  mutate(`class` = droplevels(`class`)) %>%
  select(`exit`, `class`, weight_ps, threat_experience) %>%
  group_by(`class`, `exit`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`class`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(exit = factor(exit, levels = c("no", "don't know / missing", "yes"))) %>%
  filter(class != "dont't know / not available") %>%
  ggplot(aes(x = `class`, y = share, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    )  +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

ggarrange(RACE, GENDER, CLASS, common.legend = TRUE, nrow = 1)

ggsave("~/Lab/github/incivility/svg/considering_exit_by_group.jpg", width = 24, height = 12, units = "cm")
```


```{r chisq_exit}
A <- matrix(c(1772.7 + 113.7, 155.9 + 16.7, 86.9, 18.1), ncol = 2, nrow = 2, byrow = TRUE)
B <- matrix(c(1170.1 + 56.3, 734.8 + 73.3, 61, 40.8), ncol = 2, nrow = 2, byrow = TRUE)
C <- matrix(c(682.2 + 30.2 + 912.2 + 61.6, 262.8 + 29.1, 26.9+47.4, 23.1), ncol = 2, nrow = 2, byrow = TRUE)

chisq.test(A) # X-squared = 8.6785, df = 1, p-value = 0.00322 | 
chisq.test(B) # X-squared = 1.7035e-27, df = 1, p-value = 1
chisq.test(C) # X-squared = 5.1139, df = 1, p-value = 0.02373
```

```{r chisq_noexit}
A <- matrix(c(1772.7, 155.9, 86.9 + 113.7, 18.1 + 16.7), ncol = 2, nrow = 2, byrow = TRUE)
B <- matrix(c(1170.1, 734.8, 61  + 56.3, 40.8 + 73.3), ncol = 2, nrow = 2, byrow = TRUE)
C <- matrix(c(682.2 + 30.2 + 912.2 + 61.6, 262.8, 26.9 + 47.4, 23.1 + 29.1), ncol = 2, nrow = 2, byrow = TRUE)

chisq.test(A) # X-squared = 8.6785, df = 1, p-value = 0.00322 | 
chisq.test(B) # X-squared = 1.7035e-27, df = 1, p-value = 1
chisq.test(C) # X-squared = 5.1139, df = 1, p-value = 0.02373
```


\newpage

### Figure 4: Certain descriptive characteristics and avoid topics

```{r, echo = FALSE}
GENDER <- kommrep_loc_lm %>%
  select(v_sorge_umgang4, v_geschlecht, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%

  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`avoid topics` = as.character(as_factor(v_sorge_umgang4))) %>%
  mutate(`avoid topics` = recode(
    `avoid topics`,
    `Ja` = "yes",
    `Nicht Gewählt` = "no",
    `Weiß nicht` = "don't know / missing"
  )) %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "don't know / missing", `avoid topics`)) %>%

  mutate(gender = as_factor(v_geschlecht)) %>%
  mutate(gender = recode(
    gender,
    `männlich` = "male",
    `weiblich` = "female/diverse",
    `divers` = "female/diverse",
    `weitere / andere` = "female/diverse")
  ) %>%
  mutate(gender = factor(gender, levels = c("male", "female/diverse"))) %>%
  select(gender, `avoid topics`, weight_ps, threat_experience) %>%
  group_by(gender, `avoid topics`, threat_experience) %>%
  filter(!is.na(gender)) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(gender, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("no", "don't know / missing", "yes"))) %>%
  ggplot(aes(x = gender, y = share, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    guides(fill = guide_legend(reverse = TRUE)) +  
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

RACE <- kommrep_loc_lm %>%
  select(v_sorge_umgang4, racialized, weight_ps, threat_experience) %>%
  
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%

  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`avoid topics` = as.character(as_factor(v_sorge_umgang4))) %>%
  mutate(`avoid topics` = recode(
    `avoid topics`,
    `Ja` = "yes",
    `Nicht Gewählt` = "no",
    `Weiß nicht` = "don't know / missing"
  )) %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "don't know / missing", `avoid topics`)) %>%
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  filter(!is.na(`racialized`)) %>%
  group_by(`racialized`, `avoid topics`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`racialized`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("no", "don't know / missing", "yes"))) %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  ggplot(aes(x = `racialized`, y = share, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    guides(fill = guide_legend(reverse = TRUE)) +
    ylab("percent (based on weighed cases)") +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) 

CLASS <- kommrep_loc_lm %>%
  select(v_sorge_umgang4, v_schicht, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`avoid topics` = as.character(as_factor(v_sorge_umgang4))) %>%
  mutate(`avoid topics` = recode(
    `avoid topics`,
    `Ja` = "yes",
    `Nicht Gewählt` = "no",
    `Weiß nicht` = "don't know / missing"
  )) %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "don't know / missing", `avoid topics`)) %>%
  mutate(`class` = as_factor(v_schicht)) %>%
  mutate(
    `class` = recode(
      `class`,
      `Der Oberschicht` = "upper",
      `Der oberen Mittelschicht` = "upper",
      `Der Mittelschicht` = "middle",
      `Der unteren Mittelschicht` = "lower",
      `Der Arbeiterschicht` = "lower",
      `Der Unterschicht` = "lower"
    )) %>%
  mutate(`class` = na_if(`class`, "Weiß nicht")) %>%
  filter(!is.na(class)) %>%
  mutate(`class` = droplevels(`class`)) %>%
  select(`avoid topics`, `class`, weight_ps, threat_experience) %>%
  group_by(`class`, `avoid topics`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`class`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("no", "don't know / missing", "yes"))) %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  ggplot(aes(x = `class`, y = share, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    )  +
    guides(fill = guide_legend(reverse = TRUE)) +
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggarrange(RACE, GENDER, CLASS, common.legend = TRUE, nrow = 1)

ggsave("~/Lab/github/incivility/svg/avoiding_topics_by_group.jpg", width = 24, height = 12, units = "cm")
```

```{r}
A <- matrix(c(394.4 + 1381.4, 38.9+130.6, 197.6, 21.1), ncol = 2, nrow = 2, byrow = TRUE)
B <- matrix(c(222.8 + 960, 203.5+533.2, 104.6, 112.1), ncol = 2, nrow = 2, byrow = TRUE)
C <- matrix(c(136.7+524.8+201+3+721, 37.1+205.4, 77.8+98.9,36.5), ncol = 2, nrow = 2, byrow = TRUE)

chisq.test(A) # X-squared = 0.11328, df = 1, p-value = 0.7364
chisq.test(B) # X-squared = 13.942, df = 1, p-value = 0.0001886
chisq.test(C) # X-squared = 2.0975, df = 1, p-value = 0.1475
```

\newpage

## Table 1: Bivariate Correlations

```{r bivariate_correlations, echo = FALSE, warning = FALSE}
depvars <- c(
  "stay", # certainty to stay = descriptive representation
  "muted2" # substantive representation
)

ivars <- c(
  threat_verbal = "Communicative threat",
  threat_physical = "Physical threat", 
  racialized = "Racialised group",
  female_diverse = "Female or diverse",
  class_normalized = "Class",
  div = "Primary Topic: Migration", 
  gen = "Primary Topic: Gender",
  soc = "Primary Topic: Class"
)

bind_rows(
  lapply(
    names(ivars),
    function(ivar){
      lapply(
        depvars,
        function(depvar){
          y <- cor.test(
            x = as.numeric(kommrep_loc_lm[[ivar]]),
            y = as.numeric(kommrep_loc_lm[[depvar]]),
            method = "pearson",
            # method = "spearman",
            exact = FALSE,
            alternative = "two.sided"
          )
          cases = sum(apply(
            matrix(
            data = c(
              as.numeric(kommrep_loc_lm[[ivar]]),
              as.numeric(kommrep_loc_lm[[depvar]])
            ),
            ncol = 2, 
            byrow = FALSE
          ),
          1,
          function(row) !any(is.na(row))
          ))
          tibble(
            ivar = ivar,
            depvar = depvar,
            rho = y$estimate,
            p.value = y$p.value,
            n = cases
          )
        }
      )
    }
  )
) %>%
  mutate(stars = ifelse(p.value < .05, "*", "")) %>%
  mutate(stars = ifelse(p.value < .01, "**", stars)) %>%
  mutate(stars = ifelse(p.value < .001, "***", stars)) %>%
  mutate(combined = paste0(round(rho, 2), stars, "\n(n=", n, ")")) %>%
  select(`ivar`, depvar, combined) %>%
  pivot_wider(names_from = "depvar", values_from = combined) %>%
  mutate(ivar = ivars[ivar]) %>%
  rename(
    `certainty to stay` = "stay",
    `avoid topics` = "muted2",
    ` ` = "ivar"
  ) %>%
  as_flextable(show_coltype = FALSE) %>%
  add_footer_lines("* p < 0.5, ** p < .01, *** p < .001")
```

\newpage

### Table 2: Regression for Implications to descriptive Representation (Considering exit) 

```{r descriptive_representation, results = "asis", echo = FALSE}
stay1 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

stay2a <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + racialized,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

stay2b <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + racialized  + class_normalized,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

stay2c <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

stay3 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized + soc + gen + div,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

modelsummary::modelsummary(
  models = list(
    A = stay1,
    B = stay2a,
    C = stay2b,
    D = stay2c,
    E = stay3
  ),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  output = "latex",
  coef_map = c(
    "threat_verbal" = "Communicative threat ",
    "threat_physical" = "Physical threat",
    "racializedTRUE" = "Racialized group (Ref. no)",
    "female_diverseTRUE" = "Female or diverse (Ref. no)",
    "class_normalized" = "Class",
    "divTRUE" = "Primary Topic: Migration",
    "genTRUE" = "Primary Topic: Gender",
    "socTRUE" = "Primary Topic: Class",
    "AfDTRUE" = "AfD (Ref. other)",
    "SPDTRUE" = "SPD",
    "GRUENETRUE" = "B'90/Grüne",
    "LINKETRUE" = "LINKE",
    "age" = "Age",
    "(Intercept)" = "(Intercept)"
  ),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  title = "Descriptive representation: Determinants of certainty to stay"
  # , gof_omit = "BIC|AIC|RMSE|Log.Lik|F"
)
```

\newpage

### Table 3: Regression for Implications to substantive Representation (Avoid topics) 

```{r, results = "asis", echo = FALSE}
behavior1 <- glm(
  muted2 ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

behavior2 <- glm(
  muted2 ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

behavior3 <- glm(
  muted2 ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized + soc + gen + div,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

modelsummary::modelsummary(
  models = list(
    A = behavior1,
    B = behavior2,
    C = behavior3
  ),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  output = "latex",
  coef_map = c(
    "threat_verbal" = "Communicative threat",
    "threat_physical" = "Physical threat",
    "racializedTRUE" = "Racialized group (Ref. no)",
    "female_diverseTRUE" = "Female or diverse (Ref. no)",
    "class_normalized" = "Class",
    "divTRUE" = "Primary Topic: Migration",
    "genTRUE" = "Primary Topic: Gender",
    "socTRUE" = "Primary Topic: Class",
    "AfDTRUE" = "AfD (Ref. other)",
    "SPDTRUE" = "SPD",
    "GRUENETRUE" = "B'90/Grüne",
    "LINKETRUE" = "LINKE",
    "age" = "Age",
    "(Intercept)" = "(Intercept)"
  ),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  title = "Substantive representation: Avoid topics"
#  , gof_omit = "BIC|AIC|RMSE|Log.Lik|F"
)
```
