---
title: "Incivility and Representation"
subtitle: Abbildungen und Tabellen
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
bibliography: literatur.bibtex
always_allow_html: yes
editor_options:
  chunk_output_type: console
---

```{r load_libraries, message = FALSE, echo = FALSE}
library(dplyr)
library(magrittr)
library(tidyr)
library(forcats)
library(haven)
library(crosstable)
library(scales)
library(ggplot2)
library(flextable)
library(openxlsx)
library(ggplot2)
library(kommrep)
library(xtable)
library(stargazer)
library(jtools)
library(broom.mixed) # to avoid later msg of loading
library(officer)
library(ggpubr)
library(kableExtra)

stopifnot(packageVersion("kommrep") >= package_version("0.4.1"))
```

```{r set_options, include = FALSE}
set_flextable_defaults(pct_digits = "#")
options("modelsummary_format_numeric_latex" = "plain")
```

```{r make modified_table, echo = FALSE, results = "asis"}
source("~/Lab/github/incivility/aux/kommrep_loc_lm.R")
```


## Research design

### Table 1: Response Rate

```{r return_rate, echo = FALSE}
db_final_fname <- "~/Data/hbs/db/HBS-Kontaktdatenbank_2022-07-21.xlsx"
db <- openxlsx::read.xlsx(xlsxFile = db_final_fname) %>% 
  filter(!is.na(Name)) %>% 
  unique()

n_representatives <- db %>% 
  nrow()

n_representatives_nomail <- db %>% 
  filter(is.na(Mailadresse)) %>% 
  nrow()

participants <- tibble(
  `population (total)` = n_representatives,
  `representatives no contact details` = sprintf(
    "%d (%g per cent)",
    n_representatives_nomail,
    round(n_representatives_nomail / n_representatives * 100, 1)
  )
)

termination_rate <- 100 - round(nrow(kommrep_loc) / nrow(kommrep) * 100, 1)
participation_rate_started <- percent(nrow(kommrep) / nrow(filter(mailout, run == 0)), accuracy = 0.1)
participation_rate_finished <- percent(nrow(kommrep_loc) / nrow(filter(mailout, run == 0)), accuracy = 0.1)

returned <- tibble(
  `Response\n(total)` = nrow(kommrep), # paper #1: 2592
  `Fully completed` = nrow(filter(kommrep, v_lastpage == 40)),
  `partially completed` = nrow(kommrep) - nrow(filter(kommrep, v_lastpage == 40)),
   # paper #1: 2166
  `Net response rate` = participation_rate_finished, 
  `Response rate` = participation_rate_started
)

flextable(returned)
```

\newpage

## Section 4: Empirical Evidence

### Figure 1: Prevalence of the implications for representation 

```{r implications, echo = FALSE}
kommrep_loc %>%
  mutate(
    `behavior_considering exit` = ifelse(as.character(as_factor(v_exit)) == "Ja", TRUE, FALSE),
#    `behavior_avoid social media` = ifelse(v_sorge_umgang3 == 1L, TRUE, FALSE), # Verzicht auf soziale Medien
    `behavior_avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE) #  Zurückhaltung bei Themen
#     `behavior_avoid places` = ifelse(v_sorge_umgang5 == 1L, TRUE, FALSE)
  ) %>%
  select(starts_with("behavior_"), weight_ps) %>%
  pivot_longer(cols = starts_with("behavior")) %>%
  mutate(name = gsub("^behavior_(.*?)$", "\\1", name)) %>%
#  mutate(value = ifelse(is.na(value), FALSE, value)) %>%
  group_by(name, value) %>%
  summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
  pivot_wider(names_from = value, values_from = n_weighed) %>%
  mutate(true_percent = round(`TRUE` / (`TRUE` + `FALSE` + `NA`) * 100, 1)) %>%
  mutate(false_percent = round(`FALSE` / (`TRUE` + `FALSE` + `NA`) * 100, 1)) %>%
  mutate(na_percent = round(`NA` / (`TRUE` + `FALSE` + `NA`) * 100, 1)) %>%
  mutate(name = factor(
    name,
    levels = c(
      "considering exit",
#      "avoid places",
#      "avoid social media",
      "avoid topics")
  )) %>%
#  tibble(category = c("responsiveness", "responsiveness", "substantive representation", "descriptive representation")) %>%
  select(- `FALSE`, -`TRUE`, -`NA`) %>%
  rename(
    `what` = "name",
    `true` = "true_percent",
    `false` = "false_percent",
    `na` = "na_percent"
  ) %>%
  pivot_longer(cols = c("true", "false", "na")) %>%
  ggplot(aes(x = what, y = value, fill = name)) +
    geom_bar(stat = "identity", position = "stack") + 
#    ylim(0, 12.5) +
    geom_text(
    aes(label = paste0(value, "%")),
    position = position_stack(0.5),    # move to center of bars
#     vjust = -1,    # nudge above top of bar
     size = 5, color = "white"
    ) + 
    xlab("Type of behavioral change") + 
    ylab("Share/percent (with case weights)")
    

ggsave("~/Lab/github/incivility/svg/behavioral_change.svg", width = 24, height = 12, units = "cm")
```

\newpage

### Table: Plain Shares

```{r plain_shares, results = "asis", echo=FALSE}
kommrep_loc_lm %>%
  select(
    threat_verbal, threat_physical,
    female_diverse,
    class,
    racialized,
    soc, gen, div,
    weight_ps
  ) %>%
  mutate(threat_verbal_bin = ifelse(threat_verbal > 0, TRUE, FALSE)) %>%
  mutate(threat_physical_bin = ifelse(threat_physical > 0, TRUE, FALSE)) %>%
  select(-threat_verbal, -threat_physical) %>%
  
  mutate(class_lower = ifelse(class == "lower", TRUE, FALSE)) %>%
  
  # select(-weight_ps) %>%
  mutate(across(everything(), as.vector)) %>%
  pivot_longer(cols = c(threat_verbal_bin, threat_physical_bin, racialized, female_diverse, class_lower, div, gen, soc)) %>%
  group_by(name, value) %>%
  summarise(n = n(), n_weighed = sum(weight_ps), .groups = "rowwise") %>%
  select(-n) %>%
  pivot_wider(names_from = value, values_from = c(n_weighed)) %>%
  ungroup() %>%
  mutate(total = apply(as.matrix(select(., `FALSE`, `TRUE`, `NA`)), 1, sum, na.rm = TRUE)) %>%
  mutate(
    true = round(`TRUE` / total * 100, 1),
    na = round(`NA` / total * 100, 1),
    false = round(`FALSE` / total * 100, 1)
  ) %>%
  mutate(missing = ifelse(is.na(na), 0, na)) %>%
  select(name, true, missing, false) %>%
  mutate(variable = as.factor(name)) %>%
  select(-name) %>%
  mutate(variable = forcats::fct_recode(
    variable,
    `Communicative threat` = "threat_verbal_bin",
    `Physical threat` = "threat_physical_bin",
    `Racialized group` = "racialized",
    `Female or diverse` = "female_diverse",
    `Class lower` = "class_lower",
    `Primary Topic: Migration` = "div",
    `Primary Topic: Gender` = "gen",
    `Primary Topic: Class` = "soc"
  )) %>%
  mutate(
    variable = factor(
      variable,
      levels = c(
        "Communicative threat", "Physical threat",
        "Racialized group", "Female or diverse", "Class lower",
        "Primary Topic: Migration", "Primary Topic: Gender", "Primary Topic: Class"
      )
    )
  ) %>%
  mutate(
    true = paste0(true, "%"),
    missing = paste0(missing, "%"),
    false = paste0(false, "%")
  ) %>%
  mutate(missing = ifelse(missing == "0%", "---", missing)) %>%
  arrange(variable) %>%
  relocate(variable) %>% 
  as_flextable(show_coltype = FALSE) %>%
  add_footer_lines("* Percent/shares calculated using case weights")
```

\newpage

### Figure 2: Threat experience and implications for representation

```{r threat_and_change3, echo = FALSE}
threat_and_change <- kommrep_loc_lm %>%
  select(threat_verbal, threat_physical, v_sorge_umgang4, v_exit, weight_ps) %>%
  
  mutate(`communicative threat` = ifelse(threat_verbal > 0, "yes", "no")) %>% 
  mutate(`communicative threat` = ifelse(is.na(`communicative threat`), "no", `communicative threat`)) %>% 
  
  mutate(`physical threat` = ifelse(threat_physical > 0, "yes", "no")) %>% 
  mutate(`physical threat` = ifelse(is.na(`physical threat`), "no", `physical threat`)) %>% 
  
  mutate(`considering exit` = ifelse(as.character(as_factor(v_exit)) == "Ja", "yes", "no")) %>%
  mutate(`considering exit` = ifelse(is.na(`considering exit`), "na", `considering exit`)) %>%
  
  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, "yes", "no")) %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "na", `avoid topics`)) %>%
  
  select(
    `communicative threat`, `physical threat`,
    `avoid topics`, `considering exit`,
    `weight_ps`
  )


bind_rows(
  list(
    threat_and_change %>%
      select(`considering exit`, `communicative threat`, weight_ps) %>%
      group_by(`considering exit`, `communicative threat`) %>%
      summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
      mutate(behavior = "considering exit") %>%
      mutate(threat = "communicative threat") %>%
      ungroup() %>%
      mutate(percent = round(n_weighed / sum(n_weighed) * 100, 1)) %>%
      rename(`behavioral effect` = "considering exit") %>%
      rename(`threat applicable` = "communicative threat") %>%
      select(-n_weighed),
    
    threat_and_change %>%
      select(`considering exit`, `physical threat`, weight_ps) %>%
      group_by(`considering exit`, `physical threat`) %>%
      summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
      mutate(behavior = "considering exit") %>%
      mutate(threat = "physical threat") %>%
      ungroup() %>%
      mutate(percent = round(n_weighed / sum(n_weighed) * 100, 1)) %>%
      rename(`behavioral effect` = "considering exit") %>%
      rename(`threat applicable` = "physical threat") %>%
      select(-n_weighed),
    
    threat_and_change %>%
      select(`avoid topics`, `communicative threat`, weight_ps) %>%
      group_by(`avoid topics`, `communicative threat`) %>%
      summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
      mutate(behavior = "avoid topics") %>%
      mutate(threat = "communicative threat") %>%
      ungroup() %>%
      mutate(percent = round(n_weighed / sum(n_weighed) * 100, 1)) %>%
      rename(`behavioral effect` = "avoid topics") %>%
      rename(`threat applicable` = "communicative threat") %>%
      select(-n_weighed),
    
    threat_and_change %>%
      select(`avoid topics`, `physical threat`, weight_ps) %>%
      group_by(`avoid topics`, `physical threat`) %>%
      summarise(n_weighed = sum(weight_ps), .groups = "rowwise") %>%
      mutate(behavior = "avoid topics") %>%
      mutate(threat = "physical threat") %>%
      ungroup() %>%
      mutate(percent = round(n_weighed / sum(n_weighed) * 100, 1)) %>%
      rename(`behavioral effect` = "avoid topics") %>%
      rename(`threat applicable` = "physical threat") %>%
      select(-n_weighed)
  )
) %>%
  ggplot(aes(x = `threat applicable`, y = percent, fill = `behavioral effect`)) +
    geom_bar(position = "stack", stat = "identity") +
    facet_grid(behavior ~ threat) +
    geom_text(
      aes(label = paste(percent, "%")),
      position = position_stack(0.5),
      color = "white"
    )

ggsave("~/Lab/github/incivility/svg/threat_and_behavioral_change.svg", width = 24, height = 12, units = "cm")
```


```{r threat_and_change1, echo = FALSE}
crosstable_data <- kommrep_loc_lm %>%
  select(threat_verbal, threat_physical, stay, muted2) %>% # Verhaltensänderung? 1504 1=Ja!
  
  mutate(`communicative threat` = ifelse(threat_verbal > 0, "yes", "no/missing")) %>% 
  mutate(`communicative threat` = ifelse(is.na(`communicative threat`), "no/missing", `communicative threat`)) %>% 
  
  mutate(`physical threat` = ifelse(threat_physical > 0, "yes", "no/missing")) %>% 
  mutate(`physical threat` = ifelse(is.na(`physical threat`), "no/missing", `communicative threat`))

crosstable_stay <- crosstable_data %>%
  select(`communicative threat`, `physical threat`, `stay`) %>% 
  crosstable(
    by = `stay`,
    percent_digits = 1,
    showNA = "no",
    percent_pattern = list(
      body = "{p_row}\n({n})",
      total_row = "{p_row}\n({n})",
      total_col = "{p_row}\n({n})",
      total_all = "{p_row}\n({n})"
    ),
    total = "none",
  ) %>%
  as.data.frame()

crosstable_avoid_topics <- crosstable_data %>%
  select(`communicative threat`, `physical threat`, `muted2`) %>% 
  crosstable(
    by = `muted2`,
    percent_digits = 1,
    showNA = "no",
    percent_pattern = list(
      body = "{p_row}\n({n})",
      total_row = "{p_row}\n({n})",
      total_col = "{p_row}\n({n})",
      total_all = "{p_row}\n({n})"
    ),
    total = "none",
  ) %>% 
  as.data.frame()

bind_cols(
  select(crosstable_stay, -.id),
  select(crosstable_avoid_topics, `FALSE`, `TRUE`)
) %>% 
  as_flextable(show_coltype = FALSE) %>%
  merge_at(i = 1:2, j = 1) %>%
  merge_at(i = 3:4, j = 1) %>%
  set_header_labels(
    values = c(
      `label` = "",
      `variable` = "",
      `FALSE...3` = "no",
      `TRUE...4` = "yes",
      `FALSE...5` = "no",
      `TRUE...6` = "yes"
    )
  ) %>%
  add_header_row(
    top = TRUE,
    values = c("", "", "certainty to stay", "avoid topics"),
    colwidths = c(1,1, 2,2)
  ) %>% 
  hline(i = 2) %>%
  flextable::align(i = 1:2, j = 3:6, align = "center", part = "header") %>%
  fix_border_issues(part = "all") %>%
  hline_bottom(part = "footer")
```


\newpage

### Figure 3: Certain descriptive characteristics and consider exit 

```{r, echo = FALSE}
GENDER <- kommrep_loc %>%
  select(v_exit, v_geschlecht) %>%
  mutate(exit = ifelse(as.character(as_factor(v_exit)) == "Ja", TRUE, FALSE)) %>%
  mutate(gender = as_factor(v_geschlecht)) %>%
  mutate(gender = recode(
    gender,
    `männlich` = "male",
    `weiblich` = "female/diverse",
    `divers` = "female/diverse",
    `weitere / andere` = "female/diverse")
  ) %>%
  mutate(gender = factor(gender, levels = c("male", "female/diverse"))) %>%
  select(gender, `exit`) %>%
  group_by(gender, `exit`) %>%
  filter(!is.na(gender)) %>%
  summarise(N = n(), .groups = "rowwise") %>%
  group_by(gender) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`exit` = ifelse(is.na(`exit`), "NA", `exit`)) %>%
  mutate(`exit` = factor(`exit`, levels = c("FALSE", "NA", "TRUE"))) %>%
  mutate(percent = round(share * 100, 1)) %>%
  ggplot(aes(x = gender, y = percent, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(label = paste(percent, "%")), position = position_stack(0.5), color = "white") +
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

RACE <- kommrep_loc_lm %>%
  select(v_exit, racialized) %>%
  mutate(exit = ifelse(as.character(as_factor(v_exit)) == "Ja", TRUE, FALSE)) %>%
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  filter(!is.na(`racialized`)) %>%
  group_by(`racialized`, `exit`) %>%
  summarise(N = n(), .groups = "rowwise") %>%
  group_by(`racialized`) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`exit` = ifelse(is.na(`exit`), "NA", `exit`)) %>%
  mutate(`exit` = factor(`exit`, levels = c("FALSE", "NA", "TRUE"))) %>%
  mutate(percent = round(share * 100, 1)) %>%
  ggplot(aes(x = `racialized`, y = percent, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(label = paste(percent, "%")), position = position_stack(0.5), color = "white") 

CLASS <- kommrep_loc_lm %>%
  select(v_exit, class) %>%
  mutate(exit = ifelse(as.character(as_factor(v_exit)) == "Ja", TRUE, FALSE)) %>%
  filter(!is.na(class)) %>%
  mutate(`class` = droplevels(`class`)) %>%
  select(`exit`, `class`) %>%
  group_by(`class`, `exit`) %>%
  summarise(N = n(), .groups = "rowwise") %>%
  group_by(`class`) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`exit` = ifelse(is.na(`exit`), "NA", `exit`)) %>%
  mutate(`exit` = factor(`exit`, levels = c("FALSE", "NA", "TRUE"))) %>%
  mutate(percent = round(share * 100, 1)) %>%
  ggplot(aes(x = `class`, y = percent, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(label = paste(percent, "%")), position = position_stack(0.5), color = "white")  +
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggarrange(RACE, GENDER, CLASS, common.legend = TRUE, nrow = 1)

ggsave("~/Lab/github/incivility/svg/considering_exit_by_group.svg", width = 24, height = 12, units = "cm")
```


\newpage

### Figure 4: Certain descriptive characteristics and avoid topics

```{r, echo = FALSE}
GENDER <- kommrep_loc %>%
  select(v_sorge_umgang4, v_geschlecht) %>%
  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(gender = as_factor(v_geschlecht)) %>%
  mutate(gender = recode(
    gender,
    `männlich` = "male",
    `weiblich` = "female/diverse",
    `divers` = "female/diverse",
    `weitere / andere` = "female/diverse")
  ) %>%
  mutate(gender = factor(gender, levels = c("male", "female/diverse"))) %>%
  select(gender, `avoid topics`) %>%
  group_by(gender, `avoid topics`) %>%
  filter(!is.na(gender)) %>%
  summarise(N = n(), .groups = "rowwise") %>%
  group_by(gender) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "NA", `avoid topics`)) %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("FALSE", "NA", "TRUE"))) %>%
  mutate(percent = round(share * 100, 1)) %>%
  ggplot(aes(x = gender, y = percent, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(label = paste(percent, "%")), position = position_stack(0.5), color = "white") +
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

RACE <- kommrep_loc_lm %>%
  select(v_sorge_umgang4, racialized) %>%
  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  filter(!is.na(`racialized`)) %>%
  group_by(`racialized`, `avoid topics`) %>%
  summarise(N = n(), .groups = "rowwise") %>%
  group_by(`racialized`) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "NA", `avoid topics`)) %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("FALSE", "NA", "TRUE"))) %>%
  mutate(percent = round(share * 100, 1)) %>%
  ggplot(aes(x = `racialized`, y = percent, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(label = paste(percent, "%")), position = position_stack(0.5), color = "white") 

CLASS <- kommrep_loc %>%
  select(v_sorge_umgang4, v_schicht) %>%
  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`class` = as_factor(v_schicht)) %>%
  mutate(
    `class` = recode(
      `class`,
      `Der Oberschicht` = "upper",
      `Der oberen Mittelschicht` = "upper",
      `Der Mittelschicht` = "middle",
      `Der unteren Mittelschicht` = "lower",
      `Der Arbeiterschicht` = "lower",
      `Der Unterschicht` = "lower"
    )) %>%
  mutate(`class` = na_if(`class`, "Weiß nicht")) %>%
  filter(!is.na(class)) %>%
  mutate(`class` = droplevels(`class`)) %>%
  select(`avoid topics`, `class`) %>%
  group_by(`class`, `avoid topics`) %>%
  summarise(N = n(), .groups = "rowwise") %>%
  group_by(`class`) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "NA", `avoid topics`)) %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("FALSE", "NA", "TRUE"))) %>%
  mutate(percent = round(share * 100, 1)) %>%
  ggplot(aes(x = `class`, y = percent, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    geom_text(aes(label = paste(percent, "%")), position = position_stack(0.5), color = "white")  +
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggarrange(RACE, GENDER, CLASS, common.legend = TRUE, nrow = 1)

ggsave("~/Lab/github/incivility/svg/avoiding_topics_by_group.svg", width = 24, height = 12, units = "cm")
```

\newpage

## Table 1: Bivariate Correlations

```{r bivariate_correlations, echo = FALSE, warning = FALSE}
depvars <- c(
  "stay", # certainty to stay = descriptive representation
  "muted2" # substantive representation
)

ivars <- c(
  threat_verbal = "Communicative threat",
  threat_physical = "Physical threat", 
  racialized = "Racialised group",
  female_diverse = "Female or diverse",
  class_normalized = "Class",
  div = "Primary Topic: Migration", 
  gen = "Primary Topic: Gender",
  soc = "Primary Topic: Class"
)

bind_rows(
  lapply(
    names(ivars),
    function(ivar){
      lapply(
        depvars,
        function(depvar){
          y <- cor.test(
            x = as.numeric(kommrep_loc_lm[[ivar]]),
            y = as.numeric(kommrep_loc_lm[[depvar]]),
            method = "pearson",
            # method = "spearman",
            exact = FALSE,
            alternative = "two.sided"
          )
          cases = sum(apply(
            matrix(
            data = c(
              as.numeric(kommrep_loc_lm[[ivar]]),
              as.numeric(kommrep_loc_lm[[depvar]])
            ),
            ncol = 2, 
            byrow = FALSE
          ),
          1,
          function(row) !any(is.na(row))
          ))
          tibble(
            ivar = ivar,
            depvar = depvar,
            rho = y$estimate,
            p.value = y$p.value,
            n = cases
          )
        }
      )
    }
  )
) %>%
  mutate(stars = ifelse(p.value < .05, "*", "")) %>%
  mutate(stars = ifelse(p.value < .01, "**", stars)) %>%
  mutate(stars = ifelse(p.value < .001, "***", stars)) %>%
  mutate(combined = paste0(round(rho, 2), stars, "\n(n=", n, ")")) %>%
  select(`ivar`, depvar, combined) %>%
  pivot_wider(names_from = "depvar", values_from = combined) %>%
  mutate(ivar = ivars[ivar]) %>%
  rename(
    `certainty to stay` = "stay",
    `avoid topics` = "muted2",
    ` ` = "ivar"
  ) %>%
  as_flextable(show_coltype = FALSE) %>%
  add_footer_lines("* p < 0.5, ** p < .01, *** p < .001")
```

\newpage

### Table 2: Regression for Implications to descriptive Representation (Considering exit) 

```{r descriptive_representation, results = "asis", echo = FALSE}
stay1 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

stay2 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

stay3 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized + soc + gen + div,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

modelsummary::modelsummary(
  models = list(
    A = stay1,
    B = stay2,
    C = stay3
  ),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  output = "latex",
  coef_map = c(
    "threat_verbal" = "Communicative threat ",
    "threat_physical" = "Physical threat",
    "racializedTRUE" = "Racialized group (Ref. no)",
    "female_diverseTRUE" = "Female or diverse (Ref. no)",
    "class_normalized" = "Class",
    "divTRUE" = "Primary Topic: Migration",
    "genTRUE" = "Primary Topic: Gender",
    "socTRUE" = "Primary Topic: Class",
    "AfDTRUE" = "AfD (Ref. other)",
    "SPDTRUE" = "SPD",
    "GRUENETRUE" = "B'90/Grüne",
    "LINKETRUE" = "LINKE",
    "age" = "Age",
    "(Intercept)" = "(Intercept)"
  ),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  title = "Descriptive representation: Determinants of certainty to stay"
  # , gof_omit = "BIC|AIC|RMSE|Log.Lik|F"
)
```

\newpage

### Table 3: Regression for Implications to substantive Representation (Avoid topics) 

```{r, results = "asis", echo = FALSE}
behavior1 <- glm(
  muted2 ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

behavior2 <- glm(
  muted2 ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

behavior3 <- glm(
  muted2 ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class_normalized + racialized + soc + gen + div,
  data = kommrep_loc_lm,
  family = binomial("logit")
)

modelsummary::modelsummary(
  models = list(
    A = behavior1,
    B = behavior2,
    C = behavior3
  ),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  output = "latex",
  coef_map = c(
    "threat_verbal" = "Communicative threat",
    "threat_physical" = "Physical threat",
    "racializedTRUE" = "Racialized group (Ref. no)",
    "female_diverseTRUE" = "Female or diverse (Ref. no)",
    "class_normalized" = "Class",
    "divTRUE" = "Primary Topic: Migration",
    "genTRUE" = "Primary Topic: Gender",
    "socTRUE" = "Primary Topic: Class",
    "AfDTRUE" = "AfD (Ref. other)",
    "SPDTRUE" = "SPD",
    "GRUENETRUE" = "B'90/Grüne",
    "LINKETRUE" = "LINKE",
    "age" = "Age",
    "(Intercept)" = "(Intercept)"
  ),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  title = "Substantive representation: Avoid topics"
#  , gof_omit = "BIC|AIC|RMSE|Log.Lik|F"
)
```
