---
title: "Threatened Representation"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
bibliography: literatur.bibtex
always_allow_html: true
classoption: landscape
editor_options: 
  chunk_output_type: console
---

```{r load_libraries, message = FALSE, echo = FALSE}
library(dplyr)
library(data.table)
library(xts)
library(haven)
library(magrittr)
library(tidyr)
library(xtable)
library(forcats)
library(scales)
library(crosstable)
library(stargazer)
library(jtools)
library(broom.mixed) # to avoid later msg of loading
library(ggplot2)
library(flextable)
library(officer)
library(scales)
library(stargazer)
library(openxlsx)

library(kommrep)
stopifnot(packageVersion("kommrep") >= package_version("0.3.8"))
```

```{r set_options, include = FALSE}
set_flextable_defaults(pct_digits = "#")
options("modelsummary_format_numeric_latex" = "plain")
```

```{r make modified_table, echo = FALSE, results = "asis"}
source("~/Lab/github/incivility/aux/kommrep_loc_lm.R")
```

## Datenbericht

## Population of representatives contacted

<!-- values computed from DB, different from report #1 -->

```{r grundgesamtheit, echo = FALSE, fig.width = 8}
db <- openxlsx::read.xlsx(xlsxFile = db_final_fname) %>% 
  filter(!is.na(Name)) %>% 
  unique()

n_representatives <- db %>% 
  nrow()

n_representatives_nomail <- db %>% 
  filter(is.na(Mailadresse)) %>% 
  nrow()
```

Grundgesamtheit: `r n_representatives`
nicht erreichbar: `r n_representatives_nomail`


\newpage

## Rücklaufquote

```{r return_rate, echo = FALSE}
db <- openxlsx::read.xlsx(xlsxFile = db_final_fname) %>% 
  filter(!is.na(Name)) %>% 
  unique()

n_representatives <- db %>% 
  nrow()

n_representatives_nomail <- db %>% 
  filter(is.na(Mailadresse)) %>% 
  nrow()

participants <- tibble(
  `population (total)` = n_representatives,
  `representatives no contact details` = sprintf(
    "%d (%g per cent)",
    n_representatives_nomail,
    round(n_representatives_nomail / n_representatives * 100, 1)
  )
)

termination_rate <- 100 - round(nrow(kommrep_loc) / nrow(kommrep) * 100, 1)
participation_rate_started <- percent(nrow(kommrep) / nrow(filter(mailout, run == 0)), accuracy = 0.1)
participation_rate_finished <- percent(nrow(kommrep_loc) / nrow(filter(mailout, run == 0)), accuracy = 0.1)

returned <- tibble(
  `Response\n(total)` = nrow(kommrep), # paper #1: 2592
  `Fully completed` = nrow(filter(kommrep, v_lastpage == 40)),
  `partially completed` = nrow(kommrep) - nrow(filter(kommrep, v_lastpage == 40)),
   # paper #1: 2166
  `Net response rate` = participation_rate_finished, 
  `Response rate` = participation_rate_started
)

flextable(returned)
```

\newpage

\newpage

### Figure 3: Certain descriptive characteristics and consider exit 

```{r, echo = FALSE}
GENDER <- kommrep_loc_lm %>%
  select(
    v_exit,
    v_geschlecht,
    weight_ps,
    threat_experience
  ) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(exit = as.character(as_factor(v_exit))) %>%
  mutate(exit = recode(
    exit,
    `Ja` = "yes",
    `Nein` = "no",
    "Weiß nicht" = "don't know / missing"
  )) %>%
  mutate(exit = ifelse(is.na(exit), "don't know / missing", exit)) %>%
  mutate(gender = as_factor(v_geschlecht)) %>%
  mutate(gender = recode(
    gender,
    `männlich` = "male",
    `weiblich` = "female/diverse",
    `divers` = "female/diverse",
    `weitere / andere` = "female/diverse")
  ) %>%
  mutate(gender = factor(gender, levels = c("male", "female/diverse"))) %>%
  select(gender, `exit`, weight_ps, threat_experience) %>%
  group_by(gender, `exit`, threat_experience) %>%
  filter(!is.na(gender)) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(gender, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(exit = factor(exit, levels = c("no", "don't know / missing", "yes"))) %>%
  ggplot(aes(x = gender, y = share, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

RACE <- kommrep_loc_lm %>%
  select(v_exit, racialized, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(exit = as.character(as_factor(v_exit))) %>%
  mutate(exit = recode(
    exit,
    `Ja` = "yes",
    `Nein` = "no",
    "Weiß nicht" = "don't know / missing"
  )) %>%
  mutate(exit = ifelse(is.na(exit), "don't know / missing", exit)) %>%
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  filter(!is.na(`racialized`)) %>%
  group_by(`racialized`, `exit`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`racialized`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(exit = factor(exit, levels = c("no", "don't know / missing", "yes"))) %>%
  ggplot(aes(x = `racialized`, y = share, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) +
    ylab("percent (based on weighed cases)")

CLASS <- kommrep_loc_lm %>%
  select(v_exit, class, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(exit = as.character(as_factor(v_exit))) %>%
  mutate(exit = recode(
    exit,
    `Ja` = "yes",
    `Nein` = "no",
    "Weiß nicht" = "don't know / missing"
  )) %>%
  mutate(exit = ifelse(is.na(exit), "don't know / missing", exit)) %>%
  mutate(`class` = droplevels(`class`)) %>%
  select(`exit`, `class`, weight_ps, threat_experience) %>%
  group_by(`class`, `exit`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`class`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(exit = factor(exit, levels = c("no", "don't know / missing", "yes"))) %>%
  filter(class != "dont't know / not available") %>%
  ggplot(aes(x = `class`, y = share, fill = `exit`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    )  +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    theme(axis.title.y = element_blank(),
        axis.text.y = element_blank(),
        axis.ticks.y = element_blank())

ggarrange(RACE, GENDER, CLASS, common.legend = TRUE, nrow = 1)

ggsave("~/Lab/github/incivility/svg/considering_exit_by_group.jpg", width = 24, height = 12, units = "cm")
```

\newpage

```{r chisq_exit}
A <- matrix(c(1772.7 + 113.7, 155.9 + 16.7, 86.9, 18.1), ncol = 2, nrow = 2, byrow = TRUE)
B <- matrix(c(1170.1 + 56.3, 734.8 + 73.3, 61, 40.8), ncol = 2, nrow = 2, byrow = TRUE)
C <- matrix(c(682.2 + 30.2 + 912.2 + 61.6, 262.8 + 29.1, 26.9+47.4, 23.1), ncol = 2, nrow = 2, byrow = TRUE)

chisq.test(A) # X-squared = 8.6785, df = 1, p-value = 0.00322 | 
chisq.test(B) # X-squared = 1.7035e-27, df = 1, p-value = 1
chisq.test(C) # X-squared = 5.1139, df = 1, p-value = 0.02373
```

```{r chisq_noexit}
A <- matrix(c(1772.7, 155.9, 86.9 + 113.7, 18.1 + 16.7), ncol = 2, nrow = 2, byrow = TRUE)
B <- matrix(c(1170.1, 734.8, 61  + 56.3, 40.8 + 73.3), ncol = 2, nrow = 2, byrow = TRUE)
C <- matrix(c(682.2 + 30.2 + 912.2 + 61.6, 262.8, 26.9 + 47.4, 23.1 + 29.1), ncol = 2, nrow = 2, byrow = TRUE)

chisq.test(A) # X-squared = 8.6785, df = 1, p-value = 0.00322 | 
chisq.test(B) # X-squared = 1.7035e-27, df = 1, p-value = 1
chisq.test(C) # X-squared = 5.1139, df = 1, p-value = 0.02373
```


\newpage

### Figure 4: Certain descriptive characteristics and avoid topics

```{r, echo = FALSE}
GENDER <- kommrep_loc_lm %>%
  select(v_sorge_umgang4, v_geschlecht, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%

  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`avoid topics` = as.character(as_factor(v_sorge_umgang4))) %>%
  mutate(`avoid topics` = recode(
    `avoid topics`,
    `Ja` = "yes",
    `Nicht Gewählt` = "no",
    `Weiß nicht` = "don't know / missing"
  )) %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "don't know / missing", `avoid topics`)) %>%

  mutate(gender = as_factor(v_geschlecht)) %>%
  mutate(gender = recode(
    gender,
    `männlich` = "male",
    `weiblich` = "female/diverse",
    `divers` = "female/diverse",
    `weitere / andere` = "female/diverse")
  ) %>%
  mutate(gender = factor(gender, levels = c("male", "female/diverse"))) %>%
  select(gender, `avoid topics`, weight_ps, threat_experience) %>%
  group_by(gender, `avoid topics`, threat_experience) %>%
  filter(!is.na(gender)) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(gender, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("no", "don't know / missing", "yes"))) %>%
  ggplot(aes(x = gender, y = share, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    guides(fill = guide_legend(reverse = TRUE)) +  
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

RACE <- kommrep_loc_lm %>%
  select(v_sorge_umgang4, racialized, weight_ps, threat_experience) %>%
  
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%

  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`avoid topics` = as.character(as_factor(v_sorge_umgang4))) %>%
  mutate(`avoid topics` = recode(
    `avoid topics`,
    `Ja` = "yes",
    `Nicht Gewählt` = "no",
    `Weiß nicht` = "don't know / missing"
  )) %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "don't know / missing", `avoid topics`)) %>%
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  filter(!is.na(`racialized`)) %>%
  group_by(`racialized`, `avoid topics`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`racialized`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("no", "don't know / missing", "yes"))) %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  ggplot(aes(x = `racialized`, y = share, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    guides(fill = guide_legend(reverse = TRUE)) +
    ylab("percent (based on weighed cases)") +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    ) 

CLASS <- kommrep_loc_lm %>%
  select(v_sorge_umgang4, v_schicht, weight_ps, threat_experience) %>%
  mutate(threat_experience = ifelse(is.na(threat_experience), TRUE, threat_experience)) %>%
  mutate(threat_experience = sprintf("Threat experience: %s", as.character(threat_experience))) %>%
  mutate(`avoid topics` = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE)) %>%
  mutate(`avoid topics` = as.character(as_factor(v_sorge_umgang4))) %>%
  mutate(`avoid topics` = recode(
    `avoid topics`,
    `Ja` = "yes",
    `Nicht Gewählt` = "no",
    `Weiß nicht` = "don't know / missing"
  )) %>%
  mutate(`avoid topics` = ifelse(is.na(`avoid topics`), "don't know / missing", `avoid topics`)) %>%
  mutate(`class` = as_factor(v_schicht)) %>%
  mutate(
    `class` = recode(
      `class`,
      `Der Oberschicht` = "upper",
      `Der oberen Mittelschicht` = "upper",
      `Der Mittelschicht` = "middle",
      `Der unteren Mittelschicht` = "lower",
      `Der Arbeiterschicht` = "lower",
      `Der Unterschicht` = "lower"
    )) %>%
  mutate(`class` = na_if(`class`, "Weiß nicht")) %>%
  filter(!is.na(class)) %>%
  mutate(`class` = droplevels(`class`)) %>%
  select(`avoid topics`, `class`, weight_ps, threat_experience) %>%
  group_by(`class`, `avoid topics`, threat_experience) %>%
  summarise(N = sum(weight_ps), .groups = "rowwise") %>%
  group_by(`class`, threat_experience) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(`avoid topics` = factor(`avoid topics`, levels = c("no", "don't know / missing", "yes"))) %>%
  mutate(value = sprintf("%s (%s)", paste0(round(share * 100, 1), "%"), round(N, 1))) %>%
  ggplot(aes(x = `class`, y = share, fill = `avoid topics`)) +
    geom_bar(stat = "identity", position = "stack") +
    facet_wrap(~ threat_experience, ncol = 1) +
    scale_fill_manual(values = RColorBrewer::brewer.pal(6, "Blues")[3:5]) +
    scale_y_continuous(labels = scales::percent) +
    geom_text(
      aes(label = value),
      position = position_stack(0.5),
      color = "white",
      lineheight = .8,
      size = 3
    )  +
    guides(fill = guide_legend(reverse = TRUE)) +
    theme(axis.title.y = element_blank(),
        axis.text.y=element_blank(),
        axis.ticks.y=element_blank())

ggarrange(RACE, GENDER, CLASS, common.legend = TRUE, nrow = 1)

ggsave("~/Lab/github/incivility/svg/avoiding_topics_by_group.jpg", width = 24, height = 12, units = "cm")
```

\newpage

```{r}
A <- matrix(c(394.4 + 1381.4, 38.9+130.6, 197.6, 21.1), ncol = 2, nrow = 2, byrow = TRUE)
B <- matrix(c(222.8 + 960, 203.5+533.2, 104.6, 112.1), ncol = 2, nrow = 2, byrow = TRUE)
C <- matrix(c(136.7+524.8+201+3+721, 37.1+205.4, 77.8+98.9,36.5), ncol = 2, nrow = 2, byrow = TRUE)

chisq.test(A) # X-squared = 0.11328, df = 1, p-value = 0.7364
chisq.test(B) # X-squared = 13.942, df = 1, p-value = 0.0001886
chisq.test(C) # X-squared = 2.0975, df = 1, p-value = 0.1475
```


\newpage

## Anhänge

### Rücklaufquote nach Parteien

```{r participation_by_party, echo = FALSE, results = "asis"}
mailed_by_party <- city_party %>%
  ungroup() %>%
  select(-Stadt) %>%
  mutate(other = TOTAL - (AfD + `Bündnis 90/Die Grünen` + CDU + CSU + `Die Linke` + FDP + Piratenpartei + SPD)) %>%
  pivot_longer(everything()) %>%
  mutate(party = recode(name, `Piratenpartei` = "other")) %>%
  select(-name) %>%
  group_by(party) %>%
  summarise(total = sum(value))

returned_by_party <- kommrep_loc %>%
  mutate(party = as.character(as_factor(v_part1))) %>%
  mutate(party = replace_na(party, "other")) %>%
  mutate(party = recode(
    party,
    `Unabhängige Kandidatur, keine Partei/Wählerliste` = "other",
    `Piratenpartei` = "other",
    `Freie Wähler` = "other"
  )) %>%
  group_by(party) %>%
  summarise(participants = n()) %>%
  bind_rows(tibble(party = "TOTAL", participants = sum(.$participants))) %>%
  left_join(mailed_by_party, by = "party") %>%
  mutate(rate = round(participants / total * 100, digits = 2L)) %>% 
  mutate(dummy = 0) %>%
  mutate(dummy = ifelse(party == "other", 1L, 0L)) %>%
  mutate(dummy = ifelse(party == "TOTAL", 2L, dummy)) %>%
  arrange(dummy) %>%
  select(-dummy)

returned_by_party %>%
  flextable() %>%
  autofit() %>%
  hline(i = 7, border = officer::fp_border(style = "dotted")) %>%
  hline(i = 8)
```



```{r participation_by_party_plot, echo = FALSE}
returned_by_party %>%
  filter(party != "TOTAL") %>% 
  mutate(party = factor(party, levels = party[order(rate, decreasing = TRUE)])) %>%
  ggplot(aes(x = party, y = rate)) + 
  geom_bar(stat = "identity", fill = "cadetblue3") +
  xlab("Party") +
  ylab("Return Rate") +
  ylim(0,68) +
  geom_text(
    aes(label = sprintf("%s\n(%s/%s)", paste(round(rate, 1), "%"), participants, total)),
    vjust = -0.5,
    color = "black"
  )

ggsave("~/Lab/github/incivility/svg/return_rate_party.svg", width = 24, height = 12, units = "cm")
```


\newpage

## Inzivilität nach Geschlecht, Schicht und Migrationsbiographie

```{r, echo = FALSE}
threatened1 <- kommrep_loc %>%
  
  select(
    v_bedrohung,
    v_geschlecht,
    v_mig_background,
    v_schicht
  ) %>%
  
  mutate(`threat experience` = as_factor(v_bedrohung)) %>%
  mutate(`threat experience` = recode(
    `threat experience`,
    `Weiß nicht` = "weiß nicht / keine Antwort",
    `Ja` = "yes", `Nein` = "no"
    )
  ) %>%
  mutate(
    `threat experience` = replace_na(
      `threat experience`,
      "weiß nicht / keine Antwort")
  ) %>%
  
  mutate(sex = as_factor(v_geschlecht)) %>%
  mutate(sex = recode(
    sex,
    `divers` = "nonbinary",
    `weitere / other` = "nonbinary",
    `männlich` = "male", `weiblich` = "female",
    `weitere / andere` = "other"
  )) %>%
  
  mutate(`migration background` = ifelse(v_mig_background, "yes", "no")) %>%

  mutate(class = as_factor(v_schicht)) %>%
  mutate(
    class = recode(
      class,
      `Der Oberschicht` = "hoch",
      `Der oberen Mittelschicht` = "hoch",
      `Der Mittelschicht` = "mittel",
      `Der unteren Mittelschicht` = "niedrig",
      `Der Arbeiterschicht` = "niedrig",
      `Der Unterschicht` = "niedrig"
    )) %>%
  mutate(class = na_if(class, "Weiß nicht")) %>%
  mutate(class = droplevels(class)) %>%
  
  select(`threat experience`, sex, `migration background`, class) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(
    by = `threat experience`,
    total = "row",
    percent_digits = 0,
    showNA = "no",
    percent_pattern = list(
      body = "{n}\n({p_row})",
      total_row = "{n}\n({p_row})",
      total_col = "{n}\n({p_row})",
      total_all = "{n}\n({p_row})"
    )
  )

threatened1 %>% as_flextable(keep_id = FALSE, compact = FALSE)
```


\newpage

## Bedrohungserfahrung nach Partei

```{r threat_by_party, echo = FALSE, results = "asis", fig.width = 6}
threatened6 <- kommrep_loc %>%
  select(v_bedrohung, v_part1) %>%
  mutate(`party` = as.character(as_factor(v_part1))) %>%
  mutate(`threat experience` = as_factor(v_bedrohung)) %>%
    mutate(`threat experience` = recode(
    `threat experience`,
    `Weiß nicht` = "don't know / no response",
    `Ja` = "yes", `Nein` = "no"
    )
  ) %>%
  mutate(
    `threat experience` = replace_na(
      `threat experience`,
      "don't know / no response")
  ) %>%
  mutate(threat = as_factor(v_bedrohung)) %>%
  select(`threat experience`, `party`) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(
    by = `threat experience`,
    total = "none",
    percent_digits = 1,
    showNA = "no"
  )

threatened6 %>%
  as_flextable(
    keep_id = FALSE,
    compact = TRUE,
    fontsizes = list(body = 8, subheaders = 10, header = 10)
  )
```

\newpage

```{r threat_and_change, echo = FALSE}
behavioral_change <- kommrep_loc %>%
  select(
    v_bedrohung,
    v_sorge_umgang1
  ) %>% # Verhaltensänderung? 1504 1=Ja!
  filter(v_bedrohung != 98) %>%
  mutate(`Verhaltensänderung` = ifelse(as.vector(v_sorge_umgang1) == 0L, "ja", "nein")) %>%
  mutate(`Bedrohungserfahrung` = ifelse(as.vector(v_bedrohung) == 1L, "ja", "nein")) %>%
  crosstable(
    `Bedrohungserfahrung`, by = `Verhaltensänderung`,
    percent_pattern = list(
      body = "{p_row}\n({n})",
      total_row = "{p_row}\n({n})",
      total_col = "{p_row}\n({n})",
      total_all = "{p_row}\n({n})"
    ),
    total = "both", percent_digits = 1)


behavioral_change %>% as_flextable(keep_id = FALSE, compact = TRUE)
```

```{r threat_and_change1, echo = FALSE}
behavioral_change <- kommrep_loc_lm %>%
  select(threat_experience, threat_verbal, threat_physical, behavioral_change) %>% # Verhaltensänderung? 1504 1=Ja!
  
  mutate(`Bedrohungserfahrung` = ifelse(threat_experience, "yes", "no")) %>%
  mutate(`kommunikative Bedrohung` = ifelse(threat_verbal > 0, "yes", "no")) %>% 
  mutate(`physische Bedrohung` = ifelse(threat_physical > 0, "yes", "no")) %>% 
           
  mutate(`Verhaltensänderung` = ifelse(behavioral_change > 0, "yes", "no")) %>%
  
  select(`Bedrohungserfahrung`, `kommunikative Bedrohung`, `physische Bedrohung`, `Verhaltensänderung`) %>% 
  crosstable(
    by = `Verhaltensänderung`,
    percent_digits = 1,
    showNA = "no",
    percent_pattern = list(
      body = "{p_row}\n({n})",
      total_row = "{p_row}\n({n})",
      total_col = "{p_row}\n({n})",
      total_all = "{p_row}\n({n})"
    ),
    total = "none",
  )

behavioral_change %>% as_flextable(keep_id = FALSE, compact = FALSE)
```

\newpage

```{r threat_and_change2, echo = FALSE}
threat_and_change <- kommrep_loc_lm %>%
  select(threat_experience, threat_verbal, threat_physical, behavioral_change) %>% # Verhaltensänderung? 1504 1=Ja!
  mutate(`threat experienced` = ifelse(threat_experience, "yes", "no")) %>%
  mutate(`communicative threat` = ifelse(threat_verbal > 0, "yes", "no")) %>% 
  mutate(`physical threat` = ifelse(threat_physical > 0, "yes", "no")) %>% 
  mutate(`behavioral change` = ifelse(behavioral_change > 0, "yes", "no")) %>%
  select(`threat experienced`, `communicative threat`, `physical threat`, `behavioral change`)


lapply(
  c("communicative threat", "physical threat", "threat experienced"),
  function(threat){
    select(threat_and_change, `behavioral change`, !!threat) %>%
     group_by_all() %>%
      summarise(N = n()) %>%
      mutate(threat = !!threat) %>%
      rename("value" = !!threat) %>%
      filter(!is.na(value))
  }
) %>%
  bind_rows() %>% 
  filter(!is.na(value)) %>%
  group_by(`threat`, `value`) %>%
  group_split() %>%
  lapply(function(x) mutate(x, share = x$N / sum(x$N))) %>%
  bind_rows() %>%
  mutate(percent = round(share * 100, 1)) %>%
  ggplot(aes(x = `value`, y = percent, fill = `behavioral change`)) +
    geom_bar(position = "stack", stat = "identity") +
    facet_wrap(~ threat) +
    geom_text(
      aes(label = sprintf("%s\n[%s]", paste(percent, "%"), N)),
      position = position_stack(0.5),
      color = "white"
    )

ggsave("~/Lab/github/incivility/svg/threat_and_behavioral_change.svg", width = 24, height = 12, units = "cm")
```


    \newpage

**Tabelle 13: Behavioral Change by Group**

```{r, echo = FALSE}
change_who <- kommrep_loc %>%
  
  select(v_sorge_umgang1, v_geschlecht, v_mig_background, v_schicht) %>%
  
  mutate(`behavioral change` = ifelse(v_sorge_umgang1 == 0, "yes", "no")) %>%

  mutate(sex = as_factor(v_geschlecht)) %>%
  mutate(sex = recode(sex, `männlich` = "male", `weiblich` = "female", `divers` = "nonbinary", `weitere / andere` = "nonbinary")) %>%
  
  mutate(`migration background` = ifelse(v_mig_background, "yes", "no")) %>%

  mutate(`class` = as_factor(v_schicht)) %>%
  mutate(
    `class` = recode(
      `class`,
      `Der Oberschicht` = "high",
      `Der oberen Mittelschicht` = "high",
      `Der Mittelschicht` = "medium",
      `Der unteren Mittelschicht` = "low",
      `Der Arbeiterschicht` = "low",
      `Der Unterschicht` = "low"
    )) %>%
  mutate(`class` = na_if(`class`, "Weiß nicht")) %>%
  mutate(`class` = droplevels(`class`)) %>%
  
  select(`behavioral change`, sex, `migration background`, `class`) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(by = `behavioral change`, total = "none", percent_digits = 1, showNA = "no")

change_who %>% as_flextable(keep_id = FALSE, compact = FALSE)
```



\newpage

## Certainty to stay by sex, class, migration background

```{r echo = FALSE}
exit <- kommrep_loc_lm %>%
  
  mutate(class = as_factor(v_schicht)) %>%
  mutate(
    `subjective class` = recode(
      class,
      `Der Oberschicht` = "high",
      `Der oberen Mittelschicht` = "high",
      `Der Mittelschicht` = "medium",
      `Der unteren Mittelschicht` = "low",
      `Der Arbeiterschicht` = "low",
      `Der Unterschicht` = "low"
    )) %>%
  mutate(`subjective class` = na_if(`subjective class`, "Weiß nicht")) %>%
  mutate(`subjective class` = droplevels(`subjective class`)) %>%
  mutate(`subjective class` = as.factor(`subjective class`)) %>% 
  mutate(`subjective class` = fct_rev(`subjective class`)) %>% 

  select(stay, female_diverse, racialized, `subjective class`) %>%
  
  mutate(stay = ifelse(stay, "yes", "no / don't know")) %>%
  mutate(stay = as.factor(stay)) %>% 
  mutate(stay = fct_rev(stay)) %>% 
  
  mutate(gender = ifelse(female_diverse, "female/diverse", "male")) %>% 
  
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  mutate(`racialized` = fct_rev(as.factor(racialized))) %>% 

  
  select(-female_diverse) %>%

  crosstable(by = stay, total = "none", percent_digits = 1, showNA = "no")

exit %>% as_flextable(keep_id = FALSE, compact = FALSE)
```



\newpage

## Behavioral change by sex, class, migration backgorund

```{r, echo = FALSE}
change_who <- kommrep_loc %>%
  
  select(v_sorge_umgang1, v_geschlecht, v_mig_background, v_schicht) %>%
  
  mutate(`behavioral change` = ifelse(v_sorge_umgang1 == 0, "yes", "no")) %>%

  mutate(sex = as_factor(v_geschlecht)) %>%
  mutate(sex = recode(
    sex,
    `divers` = "nonbinary",
    `weitere / other` = "nonbinary",
    `männlich` = "male", `weiblich` = "female",
    `weitere / andere` = "other"
  )) %>%
  
  mutate(`migration background` = ifelse(v_mig_background, "yes", "no")) %>%

  mutate(class = as_factor(v_schicht)) %>%
  mutate(
    class = recode(
      class,
      `Der Oberschicht` = "high",
      `Der oberen Mittelschicht` = "high",
      `Der Mittelschicht` = "medium",
      `Der unteren Mittelschicht` = "low",
      `Der Arbeiterschicht` = "low",
      `Der Unterschicht` = "low"
    )) %>%
  mutate(class = na_if(class, "Weiß nicht")) %>%
  mutate(class = droplevels(class)) %>%
  
  select(`behavioral change`, sex, `migration background`, class) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(by = `behavioral change`, total = "none", percent_digits = 1, showNA = "no")

change_who %>% as_flextable(keep_id = FALSE, compact = FALSE)
```



\newpage

## Expected and experienced threats and behavioral change

```{r threat_and_change, echo = FALSE}
behavioral_change <- kommrep_loc_lm %>%
  select(threat_experience, threat_verbal, threat_physical, behavioral_change) %>% # Verhaltensänderung? 1504 1=Ja!
  
  mutate(`threat experienced` = ifelse(threat_experience, "yes", "no")) %>%
  mutate(`communicative threat` = ifelse(threat_verbal > 0, "yes", "no")) %>% 
  mutate(`physical threat` = ifelse(threat_physical > 0, "yes", "no")) %>% 
           
  mutate(`behavioral change` = ifelse(behavioral_change > 0, "yes", "no")) %>%
  
  select(`threat experienced`, `communicative threat`, `physical threat`, `behavioral change`) %>% 
  crosstable(
    by = `behavioral change`,
    percent_digits = 1,
    showNA = "no",
    #     percent_pattern = list(
    #   body = "{p_row}\n({n})",
    #   total_row = "{p_row}\n({n})",
    #   total_col = "{p_row}\n({n})",
    #   total_all = "{p_row}\n({n})"
    # ),
    total = "none",
  )

behavioral_change %>% as_flextable(keep_id = FALSE, compact = FALSE)
```




\newpage

## Key concerns and threat_experience

```{r key_concerns, echo = FALSE}
kommrep_loc %>% 
  select(v_bedrohung, v_sorge_umgang1, v_issue_1_recoded) %>%
  mutate(behavioral_change = ifelse(as.vector(v_sorge_umgang1) == 0L, TRUE, FALSE)) %>%
  mutate(threat_experience = ifelse(as.vector(v_bedrohung) == 1L, TRUE, FALSE)) %>% 
  #  mutate(threat_index_norm = threat_index / 6) %>%
  mutate(
    v_issue_1_min = recode(
      v_issue_1_recoded,
      `Kultur` = "art and culture",
      `Umwelt/Klima/Tierschutz` = "climate and environment",
      `Bildung/Jugend/Kinder` = "education and youth",
      `Sozialpolitik` = "social policy",
      `Sicherheit/Ordnung` = "security and order",
      `Stadtentwicklung/Verkehr/Mobilität` = "urban development",
      `Wohnen/Bau` = "urban development",
      `Gleichstellung` = "equality and diversity",
      `Wirtschaft/Finanzen` = "economy and finance",
      `Schule` = "education and youth",
      `Digitalisierung` = "digitalisation",
      `Teilhabe/Partizipation/Bürgernähe` = "participation",
      `Migration/Integration` = "migration and integration",
      `Armut/Obdachlosigkeit` = "social policy",
      `Extremismus` = "equality and diversity",
      `Diversity und Antidiskriminierung` = "equality and diversity",
      `Sport` = "sport",
      `Sozialer Zusammenhalt` = "social policy",
      `Gesundheit` = "health",
      `Europa/Internationales` = "other",
      `Sonstiges` = "other"
    )
  ) %>% 
  mutate(
    env = ifelse(v_issue_1_min == "climate and environment", TRUE, FALSE),
    edu = ifelse(v_issue_1_min == "education and youth", TRUE, FALSE),
    soc = ifelse(v_issue_1_min == "social policy", TRUE, FALSE),
    sec = ifelse(v_issue_1_min == "security and order", TRUE, FALSE),
    dev = ifelse(v_issue_1_min == "urban development", TRUE, FALSE),
    art = ifelse(v_issue_1_min == "art and culture", TRUE, FALSE),
    div = ifelse(v_issue_1_min == "equality and diversity", TRUE, FALSE),
    ec = ifelse(v_issue_1_min == "economy and finance", TRUE, FALSE),
    dig = ifelse(v_issue_1_min == "digitalisation", TRUE, FALSE),
    par = ifelse(v_issue_1_min == "participation", TRUE, FALSE),
    mig = ifelse(v_issue_1_min == "migration and integration", TRUE, FALSE),
    spo = ifelse(v_issue_1_min == "sport", TRUE, FALSE),
    san = ifelse(v_issue_1_min == "health", TRUE, FALSE)
  ) %>% 
  select(threat_experience, v_issue_1_min) %>%
  crosstable(
    by = threat_experience,
    total = "none",
    percent_digits = 0,
    showNA = "no"
  ) %>% 
  as_flextable(keep_id = FALSE, compact = TRUE)
```


\newpage

## Correlation analysis

```{r}
kommrep_loc_lm %>% 
  select(
    behavioral_change,
    stay,
    threat_verbal, 
    threat_physical,
    age,
    AfD,
    SPD, 
    GRUENE, LINKE,
    female_diverse,
    class,
    muslim,
    sintiroma,
    eastern,
    soc,
    gen,
    div
  ) %>%
  rename(
    `physical` = "threat_physical",
    `verbal` = "threat_verbal",
    `behavior` = "behavioral_change"
  ) %>% 
  cor(method = "pearson", use = "pairwise.complete.obs") %>% 
  ggcorrplot::ggcorrplot(type = "lower", method = "circle", lab_size = 0.5)
```


\newpage 

## Factor analysis of types of threats encountered

```{r}
kommrep_loc %>%
  select(-v_perzb_art6, -v_perzb_art7) %>%
  select(starts_with("v_perzb_art")) %>%
  mutate(across(everything(), as_factor)) %>%
  mutate(across(everything(), as.integer)) %>%
  mutate(across(everything(), function (x) x - 1)) %>%
  na.omit() %>% 
  factanal(2L, rotation = "varimax")

```