---
title: "Threatened Representation"
date: "`r Sys.Date()`"
output:
  pdf_document:
    latex_engine: xelatex
bibliography: literatur.bibtex
always_allow_html: true
classoption: landscape
editor_options: 
  chunk_output_type: console
---

```{r load_libraries, message = FALSE, echo = FALSE}
library(dplyr)
library(data.table)
library(xts)
library(haven)
library(magrittr)
library(tidyr)
library(xtable)
library(forcats)
library(scales)
library(crosstable)
library(stargazer)
library(jtools)
library(broom.mixed) # to avoid later msg of loading
library(ggplot2)
library(flextable)
library(officer)
library(scales)
library(stargazer)
library(openxlsx)

library(kommrep)
stopifnot(packageVersion("kommrep") >= package_version("0.3.8"))
```

```{r set_options, include = FALSE}
set_flextable_defaults(pct_digits = "#")
options("modelsummary_format_numeric_latex" = "plain")
```


```{r make modified_table, echo = FALSE, results = "asis"}
behavioral_change_index <- lapply(
  paste0("v_sorge_umgang", 2:6),
  function(var){
    x <- as.vector(kommrep_loc[[var]])
    x <- ifelse(x == 98, NA, x)
    x <- ifelse(x == 1, 1L, 0L)
  }
) %>%
  as.data.frame() %>%
  as.matrix() %>%
  apply(1, sum, na.rm = TRUE)


threat_comm_index <- lapply(
  paste0("v_perzb_art", 1:2),
  function(var){
    x <- as.vector(kommrep_loc[[var]])
    x <- ifelse(x == 98, NA, x)
    x <- x - 1
    x
  }
) %>%
  as.data.frame() %>%
  as.matrix() %>%
  apply(1, function(row) if (all(is.na(row))) NA else sum(row, na.rm = TRUE))

threat_physical_index <- lapply(
  paste0("v_perzb_art", 3:5),
  function(var){
    x <- as.vector(kommrep_loc[[var]])
    x <- ifelse(x == 98, NA, x)
    x <- x - 1
    x
  }
) %>%
  as.data.frame() %>%
  as.matrix() %>%
  apply(1, function(row) if (all(is.na(row))) NA else sum(row, na.rm = TRUE))


kommrep_loc_lm <- kommrep_loc %>%
  
  mutate(exit = as_factor(v_exit)) %>%
  mutate(stay = recode(
    exit,
    `Weiß nicht` = "FALSE",
    `Ja` = "FALSE",
    `Nein` = "TRUE"
  )) %>%
  mutate(stay = as.logical(stay)) %>%

  mutate(threat_verbal = threat_comm_index / 2) %>% 
  mutate(threat_physical = threat_physical_index / 3) %>% 
  mutate(threat_experience = ifelse(as.vector(v_bedrohung) == 1L, TRUE, FALSE)) %>% 
  
  mutate(age = 2022 - v_alter) %>%
  mutate(age = age - min(age, na.rm = TRUE)) %>% 
  mutate(age = age / max(age, na.rm = TRUE)) %>% 
  
  mutate(AfD = ifelse(party == "AfD", TRUE, FALSE)) %>%
  mutate(CDU = ifelse(party == "CDU", TRUE, FALSE)) %>%
  mutate(CSU = ifelse(party == "CSU", TRUE, FALSE)) %>%
  mutate(FW = ifelse(party == "Freie Wähler", TRUE, FALSE)) %>%
  mutate(LINKE = ifelse(party == "Die Linke", TRUE, FALSE)) %>%
  mutate(GRUENE = ifelse(party == "Bündnis 90/Die Grünen", TRUE, FALSE)) %>%
  mutate(SPD = ifelse(party == "SPD", TRUE, FALSE)) %>%
  
  mutate(asian = as.logical(as.integer(as.factor(v_out3_mmh)) - 1) | as.logical(as.integer(as.factor(v_out3_mkm)) - 1)) %>%	# Asiatisch
  mutate(asian = ifelse(is.na(asian), FALSE, asian)) %>% 
  
  mutate(jewish = as.logical(as.integer(as.factor(v_out4_mmh)) - 1) | as.logical(as.integer(as.factor(v_out4_mkm)) - 1)) %>%	# Jüdisch
  mutate(jewish = ifelse(is.na(jewish), FALSE, jewish)) %>% 
  
  mutate(muslim = as.logical(as.integer(as.factor(v_out5_mmh)) - 1)| as.logical(as.integer(as.factor(v_out5_mkm)) - 1)) %>%	# Muslimisch
  mutate(muslim = ifelse(is.na(muslim), FALSE, muslim)) %>% 
  
  mutate(sintiroma = as.logical(as.integer(as.factor(v_out6_mmh)) - 1) | as.logical(as.integer(as.factor(v_out6_mkm)) - 1)) %>%	# Sinti oder Roma
  mutate(sintiroma = ifelse(is.na(sintiroma), FALSE, sintiroma)) %>% 
  
  mutate(turkish = as.logical(as.integer(as.factor(v_out7_mmh)) - 1)| as.logical(as.integer(as.factor(v_out7_mkm)) - 1)) %>%	# Türkisch
  mutate(turkish = ifelse(is.na(turkish), FALSE, turkish)) %>% 
  
  mutate(eastern = as.logical(as.integer(as.factor(v_out8_mmh)) - 1) | as.logical(as.integer(as.factor(v_out8_mkm)) - 1)) %>%	# Osteuropäisch
  mutate(eastern = ifelse(is.na(eastern), FALSE, eastern)) %>% 
  
  mutate(black = as.logical(as.integer(as.factor(v_out9_mmh)) - 1)| as.logical(as.integer(as.factor(v_out9_mkm)) - 1)) %>%	# Schwarze Person
  mutate(black = ifelse(is.na(black), FALSE, black)) %>% 
  
  mutate(muslim_turkish = muslim | turkish) %>% 
  
  mutate(racialized = asian | jewish | muslim | sintiroma | turkish | eastern | black) %>% 

  mutate(exit = as_factor(v_exit)) %>%
  mutate(exit = ifelse(exit == "Weiß nicht", NA, exit)) %>%
  mutate(exit = !as.logical(as.integer(exit) - 1)) %>% 
  
  mutate(behavioral_change = behavioral_change_index / 5) %>%
  mutate(behavioral_change = ifelse(
    as.vector(v_sorge_umgang1) == 0L, TRUE, FALSE)
  ) %>%
  
  mutate(female_diverse = as_factor(v_geschlecht)) %>% 
  mutate(female_diverse = recode(
    female_diverse,
    `weiblich` = "TRUE",
    `männlich` = "FALSE",
    `divers` = "TRUE",
    `weitere / andere` = "TRUE"
  )) %>%
  mutate(female_diverse = as.logical(female_diverse)) %>%

  mutate(class = ifelse(as.vector(v_schicht) != 98, v_schicht - 1L / 6L, NA)) %>%
  
  mutate(
    # issues triggering classism
    soc = ifelse(v_issue_1_recoded %in% c("Armut/Obdachlosigkeit", "Klassismus", "Wohnen/Bau"), TRUE, FALSE), 
    
    # issues triggering sexism
    gen = ifelse(v_issue_1_recoded %in% c("Gleichstellung"), TRUE, FALSE), 
    
    # issues triggering racism
    div = ifelse(v_issue_1_recoded %in% c("Migration/Integration", "Extremismus", "Sozialer Zusammenhalt"), TRUE, FALSE) 
  )
```



\newpage

## Population of representatives contacted

<!-- values computed from DB, different from report #1 -->

```{r grundgesamtheit, echo = FALSE, fig.width = 8}
db_final_fname <- "~/Data/hbs/db/HBS-Kontaktdatenbank_2022-07-21.xlsx"
db <- openxlsx::read.xlsx(xlsxFile = db_final_fname) %>% 
  filter(!is.na(Name)) %>% 
  unique()

n_representatives <- db %>% 
  nrow()

n_representatives_nomail <- db %>% 
  filter(is.na(Mailadresse)) %>% 
  nrow()

participants <- tibble(
  `population (total)` = n_representatives,
  `representatives no contact details` = sprintf(
    "%d (%g per cent)",
    n_representatives_nomail,
    round(n_representatives_nomail / n_representatives * 100, 1)
  )
)

flextable(participants) %>% width(width = 2)
```


```{r abbruchquote, echo = FALSE}
termination_rate <- 100 - round(nrow(kommrep_loc) / nrow(kommrep) * 100, 1)
participation_rate_started <- percent(nrow(kommrep) / nrow(filter(mailout, run == 0)), accuracy = 0.1)
participation_rate_finished <- percent(nrow(kommrep_loc) / nrow(filter(mailout, run == 0)), accuracy = 0.1)
```

\newpage

## Return rate

```{r tabelle_grundgesamtheit, echo = FALSE}
returned <- tibble(
  `total` = nrow(kommrep), # paper #1: 2592
  `partial` = nrow(filter(kommrep, v_lastpage == 40)), # paper #1: 2166
  `full` = nrow(kommrep) - nrow(filter(kommrep, v_lastpage == 40))
)

flextable(returned) %>% align(i = 1, j = 1:3, align = "center")
```


\newpage

## Survey participation by party

```{r participation_by_party, echo = FALSE, results = "asis"}
mailed_by_party <- city_party %>%
  ungroup() %>%
  select(-Stadt) %>%
  mutate(other = TOTAL - (AfD + `Bündnis 90/Die Grünen` + CDU + CSU + `Die Linke` + FDP + Piratenpartei + SPD)) %>%
  pivot_longer(everything()) %>%
  mutate(party = recode(name, `Piratenpartei` = "other")) %>%
  select(-name) %>%
  group_by(party) %>%
  summarise(total = sum(value))

returned_by_party <- kommrep_loc %>%
  mutate(party = as.character(as_factor(v_part1))) %>%
  mutate(party = replace_na(party, "other")) %>%
  mutate(party = recode(
    party,
    `Unabhängige Kandidatur, keine Partei/Wählerliste` = "other",
    `Piratenpartei` = "other",
    `Freie Wähler` = "other"
  )) %>%
  group_by(party) %>%
  summarise(participants = n()) %>%
  bind_rows(tibble(party = "TOTAL", participants = sum(.$participants))) %>%
  left_join(mailed_by_party, by = "party") %>%
  mutate(rate = round(participants / total * 100, digits = 2L)) %>% 
  mutate(dummy = 0) %>%
  mutate(dummy = ifelse(party == "other", 1L, 0L)) %>%
  mutate(dummy = ifelse(party == "TOTAL", 2L, dummy)) %>%
  arrange(dummy) %>%
  select(-dummy)

returned_by_party %>%
  flextable() %>%
  autofit() %>%
  hline(i = 7, border = officer::fp_border(style = "dotted")) %>%
  hline(i = 8)
```


\newpage

## Threat experiences

```{r beleidigt, echo = FALSE, results = "asis"}
kommrep_loc_min <- kommrep_loc %>%
  select(v_bedrohung, v_geschlecht, v_mig_background, db_bundesland) %>%
  mutate(threat = as_factor(v_bedrohung)) %>%
  mutate(threat = recode(
    threat,
    `Weiß nicht` = "don't know / no response",
    `Ja` = "yes", `Nein` = "no"
    )
  ) %>%
  mutate(threat = replace_na(threat, "don't know / no response"))
  

kommrep_loc_min %>% 
  group_by(threat) %>%
  summarise(N = n()) %>%
  mutate(percent = N / sum(N)) %>%
  ggplot(aes(x = threat, y = percent, label = N)) + 
  geom_bar(stat = "identity") + 
  geom_text(
     position = position_dodge(width = .9),    # move to center of bars
     vjust = -0.5,    # nudge above top of bar
     size = 3
  ) + 
  scale_y_continuous(labels = scales::percent) +
  xlab("threat experience")
```


\newpage

## Threat experiences by sex, class, migration background

```{r, echo = FALSE}
threatened1 <- kommrep_loc %>%
  
  select(v_bedrohung, v_geschlecht, v_mig_background, v_schicht) %>%
  
  mutate(`threat experience` = as_factor(v_bedrohung)) %>%
  mutate(`threat experience` = recode(
    `threat experience`,
    `Weiß nicht` = "don't know / no response",
    `Ja` = "yes", `Nein` = "no"
    )
  ) %>%
  mutate(
    `threat experience` = replace_na(
      `threat experience`,
      "don't know / no response")
  ) %>%
  
  mutate(sex = as_factor(v_geschlecht)) %>%
  mutate(sex = recode(
    sex,
    `divers` = "nonbinary",
    `weitere / other` = "nonbinary",
    `männlich` = "male", `weiblich` = "female",
    `weitere / andere` = "other"
  )) %>%
  
  mutate(`migration background` = ifelse(v_mig_background, "yes", "no")) %>%

  mutate(class = as_factor(v_schicht)) %>%
  mutate(
    class = recode(
      class,
      `Der Oberschicht` = "high",
      `Der oberen Mittelschicht` = "high",
      `Der Mittelschicht` = "medium",
      `Der unteren Mittelschicht` = "low",
      `Der Arbeiterschicht` = "low",
      `Der Unterschicht` = "low"
    )) %>%
  mutate(class = na_if(class, "Weiß nicht")) %>%
  mutate(class = droplevels(class)) %>%
  
  select(`threat experience`, sex, `migration background`, class) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(
    by = `threat experience`,
    total = "row",
    percent_digits = 0,
    showNA = "no",
    percent_pattern = list(
      body = "{n}\n({p_row})",
      total_row = "{n}\n({p_row})",
      total_col = "{n}\n({p_row})",
      total_all = "{n}\n({p_row})"
    )
  )

threatened1 %>% as_flextable(keep_id = FALSE, compact = FALSE)
```


\newpage

## Threat experience by age

```{r, echo = FALSE}
threatened3 <- kommrep %>%
  filter(v_lastpage == 40) %>%
  select(v_bedrohung, v_alter) %>%
  
  mutate(`threat experience` = as_factor(v_bedrohung)) %>%
  mutate(`threat experience` = recode(
    `threat experience`, `Weiß nicht` = "don't know / no response")
  ) %>%
  
  mutate(`threat experience` = recode(
    `threat experience`,
    `Weiß nicht` = "don't know / no response",
    `Ja` = "yes", `Nein` = "no"
    )
  ) %>%
  
  filter(!is.na(v_alter)) %>%
  mutate(alter = 2022 - v_alter) %>%
  mutate(`age cohort` = as.character(trunc(alter / 10) * 10)) %>%
  mutate(
    `age cohort` = recode(
      `age cohort`,
      `10` = "10-19",
      `20` = "20-29",
      `30` = "30-39",
      `40` = "40-49",
      `50` = "50-59",
      `60` = "60-69",
      `70` = "70-79",
      `80` = "80-89",
      `90` = "90-99"
    )
  ) %>%
  
  select(`threat experience`, `age cohort`) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(
    by = `threat experience`,
    total = "row",
    percent_digits = 0,
    showNA = "no",
  )

threatened3 %>% as_flextable(keep_id = FALSE, compact = FALSE)
```


\newpage

## Threat experience by party

```{r threat_by_party, echo = FALSE, results = "asis", fig.width = 6}
threatened6 <- kommrep_loc %>%
  select(v_bedrohung, v_part1) %>%
  mutate(`party` = as.character(as_factor(v_part1))) %>%
  mutate(`threat experience` = as_factor(v_bedrohung)) %>%
    mutate(`threat experience` = recode(
    `threat experience`,
    `Weiß nicht` = "don't know / no response",
    `Ja` = "yes", `Nein` = "no"
    )
  ) %>%
  mutate(
    `threat experience` = replace_na(
      `threat experience`,
      "don't know / no response")
  ) %>%
  mutate(threat = as_factor(v_bedrohung)) %>%
  select(`threat experience`, `party`) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(
    by = `threat experience`,
    total = "none",
    percent_digits = 1,
    showNA = "no"
  )

threatened6 %>%
  as_flextable(
    keep_id = FALSE,
    compact = TRUE,
    fontsizes = list(body = 8, subheaders = 10, header = 10)
  )
```


\newpage

## Types of incivility by sex, class, migration background

```{r, echo = FALSE, fig.width = 8, warning = FALSE}
attacks <- kommrep_loc %>%
  
  select(starts_with("v_perzb_art"), v_geschlecht, v_mig_background, v_schicht, v_part1) %>%
  select(-v_perzb_art7, -v_perzb_art6) %>%
  
  mutate(across(starts_with("v_perzb_art"), as_factor)) %>%
  mutate(across(starts_with("v_perzb_art"), recode, `Trifft zu` = "yes", `Trifft nicht zu` = "no", `Weiß nicht` = "don't know / no reply")) %>%
  mutate(across(starts_with("v_perzb_art"), as.character)) %>%
  mutate(across(starts_with("v_perzb_art"), replace_na, "don't know / no reply")) %>%
  mutate(across(starts_with("v_perzb_art"), as.factor)) %>%
  
  mutate(sex = as_factor(v_geschlecht)) %>%
  mutate(sex = recode(sex, `divers` = "nonbinary", `weitere / other` = "nonbinary")) %>%
  
  mutate(`migration background` = ifelse(v_mig_background, "yes", "no")) %>%

  mutate(class = as_factor(v_schicht)) %>%
  mutate(
    class = recode(
      class,
      `Der Oberschicht` = "high",
      `Der oberen Mittelschicht` = "high",
      `Der Mittelschicht` = "medium",
      `Der unteren Mittelschicht` = "low",
      `Der Arbeiterschicht` = "low",
      `Der Unterschicht` = "low"
    )) %>%
  mutate(class = na_if(class, "Weiß nicht")) %>%
  mutate(class = droplevels(class)) %>%
  
  mutate(Partei = as.character(as_factor(v_part1))) %>%
  
  select(-v_geschlecht, -v_mig_background, -v_schicht, v_part1) %>%
  rename(
    LegacyComm = v_perzb_art1,
    SocMedia = v_perzb_art2,
    Encounter = v_perzb_art3,
    Damage = v_perzb_art4,
    Attack = v_perzb_art5
  ) %>%
  mutate(across(everything(), function(x) as.vector(x)))


what <- c("LegacyComm", "SocMedia", "Encounter", "Damage", "Attack")
ctbs <- lapply(
  what,
  function(var){
    attacks %>%
      select(all_of(var), sex, class, `migration background`) %>%
      crosstable(
        by = all_of(var),
        total = "both",
        percent_digits = 1,
        percent_pattern = list(
          body = "{n}\n({p_row})",
          total_row = "{n}\n({p_row})",
          total_col = "{n}\n({p_row})",
          total_all = "{n}\n({p_row})"
        ),
        showNA = "no"
      ) 
  }
)
names(ctbs) <- what

tab <- bind_cols(
  select(ctbs[[1]], -yes, -no, -`don't know / no reply`, -Total),
  as_tibble(as.data.frame(lapply(ctbs, `[[`, "yes"))),
  select(ctbs[[1]], Total)
)
total_row <- filter(tab, variable == "Total")[1,]
total_row[1,2:3] <- "Total"
tab <- bind_rows(
  filter(tab, variable != "Total"),
  total_row
)

as_flextable(
  tab,
  fontsizes = list(body = 8, subheaders = 8, header = 8)
)
```


\newpage

## Certainty to stay by sex, class, migration background

```{r, echo = FALSE}
exit <- kommrep_loc_lm %>%
  
  mutate(class = as_factor(v_schicht)) %>%
  mutate(
    `subjective class` = recode(
      class,
      `Der Oberschicht` = "high",
      `Der oberen Mittelschicht` = "high",
      `Der Mittelschicht` = "medium",
      `Der unteren Mittelschicht` = "low",
      `Der Arbeiterschicht` = "low",
      `Der Unterschicht` = "low"
    )) %>%
  mutate(`subjective class` = na_if(`subjective class`, "Weiß nicht")) %>%
  mutate(`subjective class` = droplevels(`subjective class`)) %>%
  mutate(`subjective class` = as.factor(`subjective class`)) %>% 
  mutate(`subjective class` = fct_rev(`subjective class`)) %>% 

  select(stay, female_diverse, racialized, `subjective class`) %>%
  
  mutate(stay = ifelse(stay, "yes", "no / don't know")) %>%
  mutate(stay = as.factor(stay)) %>% 
  mutate(stay = fct_rev(stay)) %>% 
  
  mutate(gender = ifelse(female_diverse, "female/diverse", "male")) %>% 
  
  mutate(`racialized` = ifelse(racialized, "yes", "no")) %>%
  mutate(`racialized` = fct_rev(as.factor(racialized))) %>% 

  
  select(-female_diverse) %>%

  crosstable(by = stay, total = "none", percent_digits = 1, showNA = "no")

exit %>% as_flextable(keep_id = FALSE, compact = FALSE)
```


\newpage

## Expected and experienced threats and behavioral change

```{r threat_and_change, echo = FALSE}
behavioral_change <- kommrep_loc_lm %>%
  select(threat_experience, threat_verbal, threat_physical, behavioral_change) %>% # Verhaltensänderung? 1504 1=Ja!
  
  mutate(`threat experienced` = ifelse(threat_experience, "yes", "no")) %>%
  mutate(`communicative threat` = ifelse(threat_verbal > 0, "yes", "no")) %>% 
  mutate(`physical threat` = ifelse(threat_physical > 0, "yes", "no")) %>% 
           
  mutate(`behavioral change` = ifelse(behavioral_change > 0, "yes", "no")) %>%
  
  select(`threat experienced`, `communicative threat`, `physical threat`, `behavioral change`) %>% 
  crosstable(
    by = `behavioral change`,
    percent_digits = 1,
    showNA = "no",
    #     percent_pattern = list(
    #   body = "{p_row}\n({n})",
    #   total_row = "{p_row}\n({n})",
    #   total_col = "{p_row}\n({n})",
    #   total_all = "{p_row}\n({n})"
    # ),
    total = "none",
  )

behavioral_change %>% as_flextable(keep_id = FALSE, compact = FALSE)
```


\newpage

## Types of behavioral change

```{r, echo = FALSE}
change_how <- kommrep_loc %>%
  filter(v_sorge_umgang1 == 0) %>%
  mutate(
    behavior_Misstrauen = ifelse(v_sorge_umgang2 == 1L, TRUE, FALSE), # Steigerung von Misstrauen 
    behavior_Offline = ifelse(v_sorge_umgang3 == 1L, TRUE, FALSE), # Verzicht auf soziale Medien
    behavior_Schweigen = ifelse(v_sorge_umgang4 == 1L, TRUE, FALSE), #  Zurückhaltung bei Themen
    behavior_Rückzug = ifelse(v_sorge_umgang5 == 1L, TRUE, FALSE), # Meidung von Orten und Veranstaltungen
    behavior_Umzug = ifelse(v_sorge_umgang6 == 1L, TRUE, FALSE) # Wohnortwechsel
  ) %>%
  select(starts_with("behavior_")) %>%
  pivot_longer(cols = starts_with("behavior")) %>%
  mutate(name = gsub("^behavior_(.*?)$", "\\1", name)) %>%
  mutate(name = recode(
    name,
    `Misstrauen` = "Distrust",
    `Rückzug` = "Retreat",
    `Schweigen` = "Silence",
    `Umzug` = "Move houses"
    )
  ) %>% 
  crosstable(by = value, percent_digits = 1)

change_how %>% as_flextable(keep_id = FALSE, compact = TRUE)
```


\newpage

## Behavioral change by sex, class, migration backgorund

```{r, echo = FALSE}
change_who <- kommrep_loc %>%
  
  select(v_sorge_umgang1, v_geschlecht, v_mig_background, v_schicht) %>%
  
  mutate(`behavioral change` = ifelse(v_sorge_umgang1 == 0, "yes", "no")) %>%

  mutate(sex = as_factor(v_geschlecht)) %>%
  mutate(sex = recode(
    sex,
    `divers` = "nonbinary",
    `weitere / other` = "nonbinary",
    `männlich` = "male", `weiblich` = "female",
    `weitere / andere` = "other"
  )) %>%
  
  mutate(`migration background` = ifelse(v_mig_background, "yes", "no")) %>%

  mutate(class = as_factor(v_schicht)) %>%
  mutate(
    class = recode(
      class,
      `Der Oberschicht` = "high",
      `Der oberen Mittelschicht` = "high",
      `Der Mittelschicht` = "medium",
      `Der unteren Mittelschicht` = "low",
      `Der Arbeiterschicht` = "low",
      `Der Unterschicht` = "low"
    )) %>%
  mutate(class = na_if(class, "Weiß nicht")) %>%
  mutate(class = droplevels(class)) %>%
  
  select(`behavioral change`, sex, `migration background`, class) %>%
  mutate(across(everything(), as.vector)) %>%
  crosstable(by = `behavioral change`, total = "none", percent_digits = 1, showNA = "no")

change_who %>% as_flextable(keep_id = FALSE, compact = FALSE)
```


\newpage

## Key concerns and threat_experience

```{r key_concerns, echo = FALSE}
kommrep_loc %>% 
  select(v_bedrohung, v_sorge_umgang1, v_issue_1_recoded) %>%
  mutate(behavioral_change = ifelse(as.vector(v_sorge_umgang1) == 0L, TRUE, FALSE)) %>%
  mutate(threat_experience = ifelse(as.vector(v_bedrohung) == 1L, TRUE, FALSE)) %>% 
  #  mutate(threat_index_norm = threat_index / 6) %>%
  mutate(
    v_issue_1_min = recode(
      v_issue_1_recoded,
      `Kultur` = "art and culture",
      `Umwelt/Klima/Tierschutz` = "climate and environment",
      `Bildung/Jugend/Kinder` = "education and youth",
      `Sozialpolitik` = "social policy",
      `Sicherheit/Ordnung` = "security and order",
      `Stadtentwicklung/Verkehr/Mobilität` = "urban development",
      `Wohnen/Bau` = "urban development",
      `Gleichstellung` = "equality and diversity",
      `Wirtschaft/Finanzen` = "economy and finance",
      `Schule` = "education and youth",
      `Digitalisierung` = "digitalisation",
      `Teilhabe/Partizipation/Bürgernähe` = "participation",
      `Migration/Integration` = "migration and integration",
      `Armut/Obdachlosigkeit` = "social policy",
      `Extremismus` = "equality and diversity",
      `Diversity und Antidiskriminierung` = "equality and diversity",
      `Sport` = "sport",
      `Sozialer Zusammenhalt` = "social policy",
      `Gesundheit` = "health",
      `Europa/Internationales` = "other",
      `Sonstiges` = "other"
    )
  ) %>% 
  mutate(
    env = ifelse(v_issue_1_min == "climate and environment", TRUE, FALSE),
    edu = ifelse(v_issue_1_min == "education and youth", TRUE, FALSE),
    soc = ifelse(v_issue_1_min == "social policy", TRUE, FALSE),
    sec = ifelse(v_issue_1_min == "security and order", TRUE, FALSE),
    dev = ifelse(v_issue_1_min == "urban development", TRUE, FALSE),
    art = ifelse(v_issue_1_min == "art and culture", TRUE, FALSE),
    div = ifelse(v_issue_1_min == "equality and diversity", TRUE, FALSE),
    ec = ifelse(v_issue_1_min == "economy and finance", TRUE, FALSE),
    dig = ifelse(v_issue_1_min == "digitalisation", TRUE, FALSE),
    par = ifelse(v_issue_1_min == "participation", TRUE, FALSE),
    mig = ifelse(v_issue_1_min == "migration and integration", TRUE, FALSE),
    spo = ifelse(v_issue_1_min == "sport", TRUE, FALSE),
    san = ifelse(v_issue_1_min == "health", TRUE, FALSE)
  ) %>% 
  select(threat_experience, v_issue_1_min) %>%
  crosstable(
    by = threat_experience,
    total = "none",
    percent_digits = 0,
    showNA = "no"
  ) %>% 
  as_flextable(keep_id = FALSE, compact = TRUE)
```


\newpage

## Correlation analysis

```{r}
kommrep_loc_lm %>% 
  select(
    behavioral_change,
    stay,
    threat_verbal, 
    threat_physical,
    age,
    AfD,
    SPD, 
    GRUENE, LINKE,
    female_diverse,
    class,
    muslim,
    sintiroma,
    eastern,
    soc,
    gen,
    div
  ) %>%
  rename(
    `physical` = "threat_physical",
    `verbal` = "threat_verbal",
    `behavior` = "behavioral_change"
  ) %>% 
  cor(method = "pearson", use = "pairwise.complete.obs") %>% 
  ggcorrplot::ggcorrplot(type = "lower", method = "circle", lab_size = 0.5)
```

\newpage

```{r}
models <- list(
  threat = lm(
    threat_experience ~ asian + jewish + muslim + sintiroma + turkish + eastern + black,
    kommrep_loc_lm),
  comm = lm(
    threat_verbal ~ asian + jewish + muslim + sintiroma + turkish + eastern + black,
    kommrep_loc_lm),
  physical = lm(
    threat_physical ~ asian + jewish + muslim + sintiroma + turkish + eastern + black,
    kommrep_loc_lm)
)

modelsummary::modelsummary(
  models,
  estimate = "estimate",
  output = "huxtable",
  stars = TRUE,
  title = ""
)
```


\newpage

## Descriptive representation: Determinants of certainty to stay

```{r explaining_resilience, results = "asis", echo = FALSE}
m1 <- glm(
  stay ~ threat_verbal + threat_physical,
  kommrep_loc_lm,
  family = binomial("logit")
)

m2 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE,
  kommrep_loc_lm,
  family = binomial("logit")
)


m3 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class,
  kommrep_loc_lm,
  family = binomial("logit")
)

m4 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class + racialized,
  kommrep_loc_lm,
  family = binomial("logit")
)

m5 <- glm(
  stay ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class + racialized + soc + gen + div,
  kommrep_loc_lm,
  family = binomial("logit")
)

modelsummary::modelsummary(
  models = list(
    A = m1,
    B = m2,
    C = m3,
    D = m4,
    E = m5
  ),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  output = "latex",
  coef_map = c(
    "threat_verbal" = "Communicative threat ",
    "threat_physical" = "Physical threat",
    "female_diverseTRUE" = "Female or diverse (Ref. no)",
    "class" = "Class",
    "racializedTRUE" = "Racialized group (Ref. no)",
    "socTRUE" = "Primary Topic: Class",
    "genTRUE" = "Primary Topic: Gender",
    "divTRUE" = "Primary Topic: Migration",
    "age" = "Age",
    "AfDTRUE" = "AfD (Ref. other)",
    "SPDTRUE" = "SPD",
    "GRUENETRUE" = "B'90/Grüne",
    "LINKETRUE" = "LINKE",
    "(Intercept)" = "(Intercept)"
  ),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  title = ""
  #gof_omit = "BIC|AIC|RMSE|Log.Lik|F"
)
```

\newpage


```{r, results = "asis"}
m1 <- lm(
  behavioral_change ~ threat_verbal + threat_physical,
  kommrep_loc_lm
)

m2 <- lm(
  behavioral_change ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE,
  kommrep_loc_lm
)


m3 <- lm(
  behavioral_change ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class,
  kommrep_loc_lm
)

m4 <- lm(
  behavioral_change ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class + racialized,
  kommrep_loc_lm
)


m5 <- lm(
  behavioral_change ~ threat_verbal + threat_physical + age + AfD + SPD + GRUENE + LINKE + female_diverse + class + racialized + soc + gen + div,
  kommrep_loc_lm
)


# stargazer::stargazer(
#   m1, m2, m3, m4, m5,
#   type = "latex",
#   single.row = TRUE,
#   header = FALSE,
#   report = 'vc*',
#   omit.stat = c("f", "ser")
# )

modelsummary::modelsummary(
  models = list(A = m1, B = m2, C = m3, D = m4, E = m5),
  estimate = "{estimate} ({std.error}){stars}",
  statistic = NULL,
  output = "latex",
  coef_map = c(
    "threat_verbal" = "Communicative threat",
    "threat_physical" = "Physical threat",
    "female_diverseTRUE" = "Female or diverse (Ref. no)",
    "class" = "Class",
    "racializedTRUE" = "Racialized group (Ref. no)",
    "socTRUE" = "Primary Topic: Class",
    "genTRUE" = "Primary Topic: Gender",
    "divTRUE" = "Primary Topic: Migration",
    "age" = "Age",
    "AfDTRUE" = "AfD (Ref. other)",
    "SPDTRUE" = "SPD",
    "GRUENETRUE" = "B'90/Grüne",
    "LINKETRUE" = "LINKE",
    "(Intercept)" = "(Intercept)"
  ),
  stars = c('*' = .05, '**' = .01, '***' = .001),
  title = "",
  gof_omit = "BIC|AIC|RMSE|Log.Lik|F"
)

```


\newpage

## Multivariate analysis (plot)


```{r, echo = FALSE}
plot_summs(m1, m2, m3, m4, m5, colors = "Qual1")
```


\newpage 

## Factor analysis of types of threats encountered

```{r}
kommrep_loc %>%
  select(-v_perzb_art6, -v_perzb_art7) %>%
  select(starts_with("v_perzb_art")) %>%
  mutate(across(everything(), as_factor)) %>%
  mutate(across(everything(), as.integer)) %>%
  mutate(across(everything(), function (x) x - 1)) %>%
  na.omit() %>% 
  factanal(2L, rotation = "varimax")

```